---
title: "Flowcytometry_preprocessing"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "F.M. Kerckhof"
date: "`r Sys.Date()`"
output: 
  html_document: 
    code_folding: show
    highlight: zenburn
    keep_md: yes
    theme: cosmo
    toc: yes
    number_sections: true
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 4
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
### Set knitr options ----------------------------------------------------------
knitr::opts_chunk$set(echo = TRUE)
### load required packages -----------------------------------------------------
library(Phenoflow)
library(flowWorkspace)
library(ggcyto)
library(scales)
library(officer)
library(tidyverse)
### load data ------------------------------------------------------------------
allfs.orig <- read.flowSet(path="Source_data/fcsfiles/",pattern="*.fcs",
                           emptyValue = FALSE)
# currently, because of github file storage limitations, first these 
# files will need to be donwloaded from the flowRepository

sampleNames(allfs.orig)[which(grepl("reacq",sampleNames(allfs.orig)))]<-
  gsub("_reacquisition_","",
       sampleNames(allfs.orig)[which(grepl("reacq",sampleNames(allfs.orig)))])

### Custom functions -----------------------------------------------------------
syprosytoplotr <- function(x) {
  pSYPROSYTOgatetemp <- ggcyto(x, aes(x = "RL1-H", y = "BL2-H"))
  pSYPROSYTOgatetemp <- pSYPROSYTOgatetemp +
    geom_hex(bins = 256) +
    theme_bw() +
    labs_cyto("marker") +
    ggcyto_par_set(limits = "data") +
    geom_gate(polyGateSYPROSYTO,
              colour = "orangered")
  print(pSYPROSYTOgatetemp)
}

syprosscplotr <- function(x) {
  pSYPROSSCgatetemp <- ggcyto(x, aes(x = "SSC-H", y = "BL2-H"))
  pSYPROSSCgatetemp <- pSYPROSSCgatetemp +
    geom_hex(bins = 256) +
    theme_bw() + labs_cyto("marker") +
    ggcyto_par_set(limits = "data") +
    geom_gate(polyGateSYPROSSC,
              colour = "darkgreen")
  print(pSYPROSSCgatetemp)
}

### load metadata --------------------------------------------------------------
metadata_all <- readxl::read_xlsx("alexandra_meta.xlsx",sheet="to_verify")
cordillstert <- readxl::read_xlsx("Alexandra_ICC_dils_corr.xlsx",sheet=1)

#experiment 1 KP was wrongly excluded
KPexp1names <- metadata_all %>%
  dplyr::filter(target == "PROTEIN" &
                  strain == "KP" &
                  Replicateno == 1) %>%
  pull(filenames)

metadata_all[metadata_all$filenames%in%KPexp1names,]$`Toanalyze?`<-"Yes"

### data wrangling -------------------------------------------------------------
mddf.toanalyze <- metadata_all %>% dplyr::filter(`Toanalyze?`!="No")
mddf.toanalyze$experiment <- "exp1"
mddf.toanalyze$experiment[grep("exp2",mddf.toanalyze$filenames)] <- "exp2"
mddf.toanalyze$experiment[grep("EXP2",mddf.toanalyze$filenames)] <- "exp2"
mddf.toanalyze$experiment[grep("exp3",mddf.toanalyze$filenames)] <- "exp3"
mddf.toanalyze$experiment[grep("EXP3",mddf.toanalyze$filenames)] <- "exp3"
# mddf.toanalyze$filenames %in% sampleNames(allfs.orig) # all good
trans.func <- asinh
inv.func <- sinh
trans.obj <- trans_new("myAsinh", trans.func, inv.func)
chnls <- colnames(allfs.orig)[2:28]
transList <- transformerList(chnls,trans.obj)
gsall <- GatingSet(allfs.orig)
gsall <- transform(gsall, transList)
allfs_transformed <- cytoset_to_flowSet(gs_pop_get_data(gsall))

```

# Introduction

For the experiment of Pereira & Sakarika (2021) we have a few dedicated research
questions:

1.	Estimate the intact/damaged cells progression throughout time for all conditions
  - Is there significant growth in cell count throughout time? (e.g. did the bacteria actually grow in the MMMV medium) Which condition provided the highest cell count (compare also with the CDW)?
  - Evaluate how growth phase, media composition (for M. extorquens) and type of culture change the ratio between intact/damaged cells -> what we need from FM: help with gates and counts with the correct gates. We should have 3 gates: bacterium (intact), yeast (intact), damaged (both). For the intact, we would like the growth curves graphically (and the values). For the damaged, we would like only the values.

2. How does the cell size change throughout the growth? (can we get a number for this? i.e. % change?). Is this influenced by co-cultivation

3. Is it possible to see a clear separation of bacterial and yeast strains in the co-culture experiments? If so, how does the ratio bacteria/yeast vary throughout (is there a dominant species, collaboration, etc.). 

4. Evaluate how growth phase, media composition and type of culture change the ratio of nucleic acids to protein.
  - Nucleic acid intensity graph over time (SYTO62 or maybe better SYBR Green I) - separated per "condition" (strain here?) and over treatment
  - Mean intensity values as data (limited value according to FM)
  - Frequency histogram of SYPRO intensities per treatment and per time
  - Establish link between SYRPO intensity at the end and per condition and BCA measurements
  
5. Estimate PHA content throughout time for all conditions
  - BODIPY intensity graph over time - separated per "condition" (strain here?) and over treatment
  - Identify conditions with heighest relative PHA
  - Mean intensity values as data (limited value according to FM)
  
# Methods

## FCM acquisition

Data was acquired on a Thermo Scientific Attune NXT 2019 (BRxx configuration: 488nm (blue/BL) laser and 635nm (red/RL) laser). For elementary data processing, gates were set based upon certain (single-stained ) controls. Acquisition was performed at a flowrate of 100µL/min and event rates were kept below 8000 events/second (although, due to high background some BODIPY samples reached 10.000 eps) by diluting in phosphate buffered saline (Sigma). Acquisition was stopped after 75µL of volume was recorded. An initial lead-time of 15 seconds was not recorded in order to stabilize the flow.

Total cell concentration and intact cell concentration were determined by staining with SYBR Green I and SYBR Green I/Propidium Iodide respectively, as outlined in CMET SOP OPT-001. The threshold is the green fluorescence in the BL1 (530/30BP) channel. SYBR Green I was detected on BL1 (530/30BP) while propidium iodide was detected on BL3 (695/40BP).

Using the Thermo SYTO red stain sampler kit, we assessed staining efficiency and stability for SYTO60, SYTO61 and SYTO62, and decided that SYTO62 offered the best trade-off between low noise and stain stability. In assays for BODIPY and SYPRO orange, a triple-threshold was used with a (low) SSC-H threshold, followed by an appropriate threshold on the SYTO62 fluorescence (RL1:670/14BP) and a minor threshold on the fluorescence of BODIPY 493/503 (BL1:530/30BP) or SYPRO orange (BL2:574/26BP).

The events and fluorescence over time stability was closely monitored for acquisition-level stability.

## FCM data analysis and bio-informatics

To be elaborated on later

# Results

## ICC/DCC over time

### Data quality and acquisition-level cleanup

Based upon visual inspection of the relevant gates, re-acquisition of certain
samples was performed. Below we use flowAI (Monaco *et al.*, 2016) to cleanup
acquisition-level problems in the data. First, however, we need to identify only
the cellular population based upon gates.

#### Singlet gating {.tabset .tabset-pills}

Because of the documented tendency of ME and KP to aggregate, we first made sure
that only "singlet" events were considered. We can observe that the fraction of
singlet to total events *roughly* decreases over time in MMMV. 

##### In MMMV


```{r singletgating, warning=FALSE,message=FALSE,fig.cap="Fraction of singlet events in MMMV over time (colored by strain or combination). KP= Komagataella pastoris, KPME= mix of KP and ME, ME= Methylobacterium Extorquens.",cache=TRUE,cache.lazy=FALSE}
# Subset to only ICC -----------------------------------------------------------
mddf.toanalyze.ICC.MMMV <- mddf.toanalyze %>% 
                              dplyr::filter(target=="ICC"&Medium=="MMMV")
mddf.toanalyze.ICC.AMS <- mddf.toanalyze %>% 
                              dplyr::filter(target=="ICC"&Medium=="AMS")
gsICCMMMV <- gsall[mddf.toanalyze.ICC.MMMV$filenames]
gsICCAMS <- gsall[mddf.toanalyze.ICC.AMS$filenames]
fsICCMMMV <- allfs_transformed[mddf.toanalyze.ICC.MMMV$filenames]
# unique(fsApply(fsICCMMMV,function(x)x@description$`$P12V`))
# unique(fsApply(fsICCMMMV,function(x)x@description$`$P11V`))
# unique(fsApply(fsICCMMMV,function(x)x@description$`$P13V`))
# unique(fsApply(fsICCMMMV,function(x)x@description$`$P15V`))
fsICCAMS <- allfs_transformed[mddf.toanalyze.ICC.AMS$filenames]
# unique(fsApply(fsICCAMS,function(x)x@description$`$P12V`))
# unique(fsApply(fsICCAMS,function(x)x@description$`$P11V`))
# unique(fsApply(fsICCAMS,function(x)x@description$`$P13V`))
# unique(fsApply(fsICCAMS,function(x)x@description$`$P15V`))
# Design gates -----------------------------------------------------------------
## Bacterial gates -------------------------------------------------------------
sqrcutICCbact<- matrix(c(7.50, 7.50,11.0, 12.5, 12.5,
                         2.50, 7.50,7.90, 11, 5.00),
     ncol = 2,
     nrow = 5)
colnames(sqrcutICCbact) <- c("BL1-H", "BL3-H")
polyGateICCbact <- polygonGate(.gate = sqrcutICCbact, 
                               filterId = "Intact Bacterial Cells fluo")

sqrcutICCbactprim<- matrix(c(6.75, 6.75,11.5, 13.0, 13.0,
                             2.50, 7.25,9.30, 11, 5.00),
     ncol = 2,
     nrow = 5)
colnames(sqrcutICCbactprim) <- c("BL1-H", "BL3-H")
polyGateICCbactprim <- polygonGate(.gate = sqrcutICCbactprim, 
                               filterId = "Intact Bacterial Cells (primary)")

sqrcutICCbactSC<- matrix(c(8.00, 13.0, 13.0, 8.00, 
                           4.90, 5.00, 8.25, 7.10),
     ncol = 2,
     nrow = 4)
colnames(sqrcutICCbactSC) <- c("BL1-H", "SSC-H")
polyGateICCbactSC <- polygonGate(.gate = sqrcutICCbactSC, 
                                 filterId = "Bacterial Cells scatter")

sqrcutICCbactSCprim<- matrix(c(6.50, 13.0, 13.0, 6.50, 
                               4.25, 4.25, 8.15, 7.10),
     ncol = 2,
     nrow = 4)
colnames(sqrcutICCbactSCprim) <- c("BL1-H", "SSC-H")
polyGateICCbactSCprim <- polygonGate(.gate = sqrcutICCbactSCprim, 
                                 filterId = "Bacterial Cells BL1/SSC")

sqrcutICCbactSConly<- matrix(c(7.60, 10.5, 11.10, 7.60, 
                               6.35, 5.90, 8.500, 7.40),
     ncol = 2,
     nrow = 4)
colnames(sqrcutICCbactSConly) <- c("FSC-H", "SSC-H")
polyGateICCbactSConly <- polygonGate(.gate = sqrcutICCbactSConly, 
                                 filterId = "Bacterial Cells scatter alone")
## Yeast gates -----------------------------------------------------------------
sqrcutICCyeast<- matrix(c(11.0, 11.0, 14.5, 14.5,
                          6.50, 8.50, 12.0, 11.0),
     ncol = 2,
     nrow = 4)
colnames(sqrcutICCyeast) <- c("BL1-H", "BL3-H")
polyGateICCyeast <- polygonGate(.gate = sqrcutICCyeast, 
                                filterId = "Intact Yeast Cells")

sqrcutICCyeastprim<- matrix(c(9.25, 9.50, 14.5, 14.5,
                              5.00, 8.60, 13.0, 11.0),
     ncol = 2,
     nrow = 4)
colnames(sqrcutICCyeastprim) <- c("BL1-H", "BL3-H")
polyGateICCyeastprim <- polygonGate(.gate = sqrcutICCyeastprim, 
                                filterId = "Intact Yeast Cells (primary)")

sqrcutICCyeastSC<- matrix(c(10.0, 15.0, 15.0,  15.0, 10.0,
                            7.10, 7.65, 11.5,  15.0, 10.2),
     ncol = 2,
     nrow = 5)
colnames(sqrcutICCyeastSC) <- c("BL1-H", "SSC-H")
polyGateICCyeastSC <- polygonGate(.gate = sqrcutICCyeastSC, 
                                filterId = "Yeast Cells scatter")

sqrcutICCyeastSCprim<- matrix(c(10.5, 15.0, 15.0,  15.0, 12.5,
                                6.75, 7.65, 11.5,  12.5, 10.0),
     ncol = 2,
     nrow = 5)
colnames(sqrcutICCyeastSCprim) <- c("BL1-H", "SSC-H")
polyGateICCyeastSCprim <- polygonGate(.gate = sqrcutICCyeastSCprim, 
                                filterId = "Yeast Cells BL1/SSC")

sqrcutICCyeastSConly<- matrix(c(9.70, 12.0, 13.5,  13.65, 12.0,9.3,
                                6.10, 7.60, 10.0,  12.65, 10.2,7.6),
                              ncol = 2,
                              nrow = 6)
colnames(sqrcutICCyeastSConly) <- c("FSC-H", "SSC-H")
polyGateICCyeastSConly <- polygonGate(.gate = sqrcutICCyeastSConly, 
                                filterId = "Yeast Cells scatter alone")
## DCC gate --------------------------------------------------------------------
sqrcutDCC<- matrix(c(11.0, 11.0, 14.5, 14.5,
                     9.00, 13.0, 15.0, 12.0),
     ncol = 2,
     nrow = 4)
colnames(sqrcutDCC) <- c("BL1-H", "BL3-H")
polyGateDCC <- polygonGate(.gate = sqrcutDCC, filterId = "Damaged Cells")

sqrcutDCCprim<- matrix(c(8.00, 8.00, 13.5, 13.5,
                         7.00, 13.0, 15.0, 12.5),
     ncol = 2,
     nrow = 4)
colnames(sqrcutDCCprim) <- c("BL1-H", "BL3-H")
polyGateDCCprim <- polygonGate(.gate = sqrcutDCCprim,
                               filterId = "Damaged Cells (primary)")

sqrcutDCCbact<- matrix(c(7.50, 7.50, 12.5, 12.5,11.0,
                         7.50, 12.5, 12.5, 11.0,7.90),
     ncol = 2,
     nrow = 5)
colnames(sqrcutDCCbact) <- c("BL1-H", "BL3-H")
polyGateDCCbact <- polygonGate(.gate = sqrcutDCCbact, 
                               filterId = "Damaged bacterial Cells")

sqrcutDCCbactprim<- matrix(c(7.50, 7.50, 12.5, 13.0,11.5,
                             7.80, 12.5, 12.5, 11.0,9.30),
     ncol = 2,
     nrow = 5)
colnames(sqrcutDCCbactprim) <- c("BL1-H", "BL3-H")
polyGateDCCbactprim <- polygonGate(.gate = sqrcutDCCbactprim, 
                               filterId = "Damaged bacterial Cells (primary)")

## Singlet gate ----------------------------------------------------------------
sqrcutsinglets<- matrix(c(6.0, 14.5, 14.5, 6.0,
                          5.5, 14.3, 15.1, 6.2),
     ncol = 2,
     nrow = 4)
colnames(sqrcutsinglets) <- c("BL1-H", "BL1-A")
polyGatesinglets <- polygonGate(.gate = sqrcutsinglets, filterId = "Singlets")

# Add nodes to GS --------------------------------------------------------------

nodesinglets <- gs_pop_add(gsICCMMMV,polyGatesinglets)
nodesingletsa <- gs_pop_add(gsICCAMS,polyGatesinglets)

recompute(gsICCMMMV)
selset <- gsICCMMMV[sample(1:length(gsICCMMMV),9)]
selset.bact.iccams <- gsICCAMS
selset.yeast.iccmmmv <- gsICCMMMV[grep("KP_10",sampleNames(gsICCMMMV),
                                       value = TRUE)[c(1:13,15:29)]]
selset.bact.iccmmmv <- gsICCMMMV[grep("_ME_10",sampleNames(gsICCMMMV),
                                      value = TRUE)]
selset.mix.iccmmmv <- gsICCMMMV[grep("KPME_10",sampleNames(gsICCMMMV),
                                     value = TRUE)[c(1:12,14:37)]]

node1 <- gs_pop_add(gsICCMMMV,polyGateICCbactSConly,parent="Singlets")
node2 <- gs_pop_add(gsICCMMMV,polyGateICCyeastSConly,parent="Singlets")


boolf1 <- booleanFilter(`Bacterial Cells scatter alone|Yeast Cells scatter alone`)
node12<- gs_pop_add(gsICCMMMV,boolf1,parent="Singlets")

node1a <- gs_pop_add(gsICCAMS,polyGateICCbactSConly,parent="Singlets")
node2a <- gs_pop_add(gsICCAMS,polyGateICCyeastSConly,parent="Singlets")
node12a<- gs_pop_add(gsICCAMS,boolf1,parent="Singlets")


recompute(gsICCMMMV)
recompute(gsICCAMS)
recompute(selset.yeast.iccmmmv)
recompute(selset.bact.iccmmmv)
recompute(selset.bact.iccams)
recompute(selset.mix.iccmmmv)
# Optional: below you can inspect the (hierarchical) gating strategy
# plot(selset.yeast.iccmmmv)
# plot(selset.bact.iccmmmv)
# plot(selset.bact.iccams)
# plot(selset.mix.iccmmmv)

# Get singlet stats and visualize ----------------------------------------------
singletfraction <- gs_pop_get_count_fast(gsICCMMMV,statistic = "freq",
                                         subpopulations = "/Singlets")
singletfraction.md <- inner_join(singletfraction,mddf.toanalyze,
                                 by=c("name"="filenames"))
singletfraction.md$timepoint <- gsub(".*Alexandra_(t[0-9])_.*","\\1",
                                     singletfraction.md$name)
singletfraction.md$timepointnum <- as.numeric(gsub("t","",
                                              singletfraction.md$timepoint))
wbsglets <- openxlsx::createWorkbook(title="Alexandra singlets MMMV")
openxlsx::addWorksheet(wbsglets,sheetName="MMMV_singletFraction")
openxlsx::addWorksheet(wbsglets,sheetName="AMS_singletFraction")
openxlsx::writeData(wbsglets,sheet="MMMV_singletFraction",x = singletfraction.md)
# splot <- singletfraction.md %>% ggplot(aes(x=timepointnum,y=Frequency,
#                                            color=strain,fill=strain))
# splot + geom_point(size=4) + geom_smooth(se=0.5) + theme_bw()

splotbp <- singletfraction.md %>% ggplot(aes(x=timepoint,y=Frequency,
                                             fill=strain))
splotbp + geom_boxplot() + theme_bw() + facet_wrap(~strain,scale="free_y") +
          ylab("Fraction of singlets/total events") + 
          scale_fill_brewer(name="Strain or\ncombination",palette = "Dark2") +
          theme(axis.title.x = element_blank())

singletfractiona <- gs_pop_get_count_fast(gsICCAMS,statistic = "freq",
                                         subpopulations = "/Singlets")
singletfractiona.md <- inner_join(singletfractiona,mddf.toanalyze,
                                  by=c("name"="filenames"))
singletfractiona.md$timepoint <- gsub(".*Alexandra_(t[0-9])_.*","\\1",
                                      singletfractiona.md$name)
singletfractiona.md$timepointnum <- as.numeric(gsub("t","",
                                                singletfractiona.md$timepoint))
openxlsx::writeData(wbsglets,sheet="AMS_singletFraction",x = singletfractiona.md)
# splota <- singletfractiona.md %>% ggplot(aes(x=timepointnum,y=Frequency,
#                                            color=strain,fill=strain))
# splota + geom_point(size=4) + geom_smooth() + theme_bw()
openxlsx::saveWorkbook(wbsglets,
                       file="Results/SingletFraction.xlsx",
                       overwrite = TRUE)
```

##### In AMS

For cultivation of ME on AMS we observe a similar (rough) decrease:

```{r singletratiogAMS, warning=FALSE,message=FALSE,fig.cap="Fraction of singlet events in AMS over time for ME (Methylobacterium Extorquens).",cache=TRUE,cache.lazy=FALSE}
splotabp <- singletfractiona.md %>%
  ggplot(aes(x = timepoint, y = Frequency, fill = strain))
splotabp + geom_boxplot() + theme_bw() +
  ylab("Fraction of singlets/total events") +
  scale_fill_manual(name = "Strain", values = "#7570B3") +
  theme(axis.title.x = element_blank())
```


#### Singlet gating inspection {.tabset .tabset-pills}

For reference, we display 6 random samples for each singlet gating set.

##### For KP in MMMV

Clearly a lot of non-singlets could be observed for KP in MMMV

```{r KPsingletinspection, warning=FALSE,message=FALSE,fig.cap="6 randomly selected samples to demonstrate singlet gating for KP",cache=TRUE, cache.lazy=FALSE}
pICCMMVsing <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),6)] %>%
                      ggcyto(aes(x=`BL1-A`,y=`BL1-H`),subset="root")
pICCMMVsing + geom_hex(bins=256) + theme_bw() + geom_gate(polyGatesinglets)
```

##### For ME in MMMV

```{r MEsingletinspection, warning=FALSE,message=FALSE,fig.cap="6 randomly selected samples to demonstrate singlet gating for ME in MMMV",cache=TRUE, cache.lazy=FALSE}
pICCMMVsingb <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),6)] %>%
                      ggcyto(aes(x=`BL1-A`,y=`BL1-H`),subset="root")
pICCMMVsingb + geom_hex(bins=512) + theme_bw() + geom_gate(polyGatesinglets)
```

##### For ME in AMS

```{r MEamssingletinspection, warning=FALSE,message=FALSE,fig.cap="6 randomly selected samples to demonstrate singlet gating for ME in AMS",cache=TRUE, cache.lazy=FALSE}
pICCAMSsingb <- selset.bact.iccams[sample(1:length(selset.bact.iccams),6)] %>%
                      ggcyto(aes(x=`BL1-A`,y=`BL1-H`),subset="root")
pICCAMSsingb + geom_hex(bins=512) + theme_bw() + geom_gate(polyGatesinglets)
```


##### For KPME in MMV

```{r KPMEsingletinspection, warning=FALSE,message=FALSE,fig.cap="6 randomly selected samples to demonstrate singlet gating for KPME in MMMV",cache=TRUE, cache.lazy=FALSE}
pICCAMSsingmix <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),6)] %>%
                      ggcyto(aes(x=`BL1-A`,y=`BL1-H`),subset="root")
pICCAMSsingmix + geom_hex(bins=512) + theme_bw() + geom_gate(polyGatesinglets)
```

#### Scater/fluorescence gating strategy

##### Primary gating on scatter alone {.tabset .tabset-pills}

###### KP in MMMV

It is clear that based upon scatter alone we have a (minor) overlap between 
ME and KP. 

```{r ICCTCCgs_MMMV, echo=FALSE,warning=FALSE,message=FALSE,fig.cap="Example gating strategy for KP in MMMV based on primary gating for scatter alone.",cache=TRUE,cache.lazy=FALSE}
# Verify gating strategy for yeast, yeast, ICC, MMMMV---------------------------
pICCMMVsco <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`FSC-H`),subset="Singlets")
pICCMMVsco + geom_hex(bins=256) + theme_bw() + geom_gate(polyGateICCyeastSConly) + ggcyto_par_set(limits="instrument")


# use officer for slides -------------------------------------------------------
yeastscatterslides <- read_pptx()
yeastscatterslides <- add_slide(yeastscatterslides,layout = "Title Slide",
                                master = "Office Theme")
# layout_properties(yeastscatterslides,layout = "Title Slide")
yeastscatterslides <- ph_with(yeastscatterslides,
                              value="Gating manual verification slides",
                              location=ph_location_type(type="ctrTitle"))
yeastscatterslides <- ph_with(yeastscatterslides,
                              value="For check by Myrsini and Alexandra",
                              location=ph_location_type(type="subTitle"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastscatterslides <- ph_with(yeastscatterslides, value = "slide 1", 
                              location = ph_location_type(type = "sldNum"))

yeastscatterslides <- add_slide(yeastscatterslides,layout = "Section Header",
                                master = "Office Theme")

yeastscatterslides <- ph_with(yeastscatterslides,
                              value="Scatter-based primary gating for yeast MMMV",
                              location=ph_location_type(type="title"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastscatterslides <- ph_with(yeastscatterslides, value = "slide 2", 
                              location = ph_location_type(type = "sldNum"))
### yeast scatter only ---------------------------------------------------------
for(i in 1:length(selset.yeast.iccmmmv)){
  yeastscatterslides <- add_slide(yeastscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                                value = paste0("slide ",i+2), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscosingle <- as.ggplot(ggcyto(selset.yeast.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`FSC-H`),
                                        subset="Singlets") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSConly)+ 
                                   ggcyto_par_set(limits="instrument"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = piccmmmvscosingle, 
                              location = ph_location_type(type = "body"))
  
}
## bacteria scatter alone MMMV --------------------------------------------------
yeastscatterslides <- add_slide(yeastscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastscatterslides <- ph_with(yeastscatterslides,
                              value="Scatter-based primary gating for bacteria MMMV",
                              location=ph_location_type(type="title"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = "With reference gate for yeast scatter (alone)", 
                              location = ph_location_type(type = "body"))

for(i in 1:length(selset.bact.iccmmmv)){
  yeastscatterslides <- add_slide(yeastscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscosingleb <- as.ggplot(ggcyto(selset.bact.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`FSC-H`),
                                        subset="Singlets") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSConly)+
                                   geom_gate(polyGateICCbactSConly,colour="blue")+ 
                                   ggcyto_par_set(limits="instrument"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = piccmmmvscosingleb, 
                              location = ph_location_type(type = "body"))
  
}

## bacteria scatter alone AMS --------------------------------------------------
yeastscatterslides <- add_slide(yeastscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastscatterslides <- ph_with(yeastscatterslides,
                              value="Scatter-based primary gating for bacteria AMS",
                              location=ph_location_type(type="title"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = paste0("slide ",3+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.bact.iccams)){
  yeastscatterslides <- add_slide(yeastscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscosingleba <- as.ggplot(ggcyto(selset.bact.iccams[i],
                                        aes(x=`SSC-H`,y=`FSC-H`),
                                        subset="Singlets") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSConly)+
                                   geom_gate(polyGateICCbactSConly,colour="blue")+ 
                                   ggcyto_par_set(limits="instrument"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = piccmmmvscosingleba, 
                              location = ph_location_type(type = "body"))
  
}

## KPME scatter alone MMMV --------------------------------------------------
yeastscatterslides <- add_slide(yeastscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastscatterslides <- ph_with(yeastscatterslides,
                              value="Scatter-based primary gating for mix MMMV",
                              location=ph_location_type(type="title"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = paste0("slide ",5+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)+
                                               length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.mix.iccmmmv)){
  yeastscatterslides <- add_slide(yeastscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)+
                                                 length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscosingleba <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`FSC-H`),
                                        subset="Singlets") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSConly)+
                                   geom_gate(polyGateICCbactSConly,colour="blue")+ 
                                   ggcyto_par_set(limits="instrument"))
  yeastscatterslides <- ph_with(yeastscatterslides, 
                              value = piccmmmvscosingleba, 
                              location = ph_location_type(type = "body"))
  
}

print(yeastscatterslides,target="gatinginspection_singlets.pptx")


```

###### ME in MMMV

Next, we look at the gating based on only scatter for *M. extorquens* alone in MMMV

```{r memmviccscob, echo=FALSE, warning=FALSE,message=FALSE, fig.cap="Primary gating based on only scatter for *M. extorquens* alone in MMMV (singlets only).",cache=TRUE, cache.lazy=FALSE}
pICCMMVscob <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`FSC-H`),subset="Singlets")
pICCMMVscob + geom_hex(bins=256) + theme_bw() + 
              geom_gate(polyGateICCyeastSConly) +
              geom_gate(polyGateICCbactSConly,colour="blue")
```

###### ME in AMS

Next, we look at the gating based on only scatter for *M. extorquens* alone in AMS.
Here, we observe a secondary population in some samples that appears to overlap
with the gate that we would expect for *K. pastoris* (in MMMV)

```{r meamsiccscob, echo=FALSE, warning=FALSE,message=FALSE, fig.cap="Primary gating based on only scatter for *M. extorquens* alone in AMS.",cache=TRUE, cache.lazy=FALSE}
pICCAMSscob <- selset.bact.iccams[sample(1:length(selset.bact.iccams),9)] %>% 
                    ggcyto(aes(x=`SSC-H`,y=`FSC-H`),subset="Singlets")
pICCAMSscob + geom_hex(bins=256) + theme_bw() + 
              geom_gate(polyGateICCyeastSConly) +
              geom_gate(polyGateICCbactSConly,colour="blue")
```

###### Mix in MMMV

Finally, we have a look at how the *M. extorquens* and *K. pastoris* gate for scatter
capture the cellular population in MMMV.

```{r mixMMMViccscob, echo=FALSE, warning=FALSE,message=FALSE, fig.cap="Primary gating based on only scatter for the mixture in MMV.",cache=TRUE, cache.lazy=FALSE}
pICCMMVscom <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`FSC-H`),subset="root")
pICCMMVscom + geom_hex(bins=256) + theme_bw() + 
              geom_gate(polyGateICCyeastSConly) +
              geom_gate(polyGateICCbactSConly,colour="blue")
```



##### Secondary gating on scatter and fluorescence {.tabset .tabset-pills}

The above serves as a primary noise filter, next we employ the joint *K. pastoris*
and *M. extorquens* scatter-gated info to look into fluorescence based gating 

###### KP in MMMV

```{r fluorescence_gating, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of secondary gating results on KP after filtering based upon the yeast cell scatter gate.",cache=TRUE, cache.lazy=FALSE}
recompute(selset.yeast.iccmmmv)
recompute(selset.bact.iccmmmv)
recompute(selset.bact.iccams)
recompute(selset.mix.iccmmmv)

primaryscatteryeast <- gs_pop_get_gs(selset.yeast.iccmmmv,
      pop = "/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone")

pICCMMVscBL1y <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets/Yeast Cells scatter alone")
pICCMMVscBL1y + geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()

node3 <- gs_pop_add(selset.yeast.iccmmmv,polyGateICCyeastSC,
                    parent="/Singlets/Yeast Cells scatter alone")
node4 <- gs_pop_add(selset.bact.iccmmmv,polyGateICCbactSC,
                    parent="/Singlets/Bacterial Cells scatter alone")
node5 <- gs_pop_add(selset.bact.iccams,polyGateICCbactSC,
                    parent="/Singlets/Bacterial Cells scatter alone")
node6a <- gs_pop_add(selset.mix.iccmmmv,polyGateICCbactSC,
                     parent="/Singlets/Bacterial Cells scatter alone")
node6b <- gs_pop_add(selset.mix.iccmmmv,polyGateICCyeastSC,
                     parent="/Singlets/Yeast Cells scatter alone")

boolf2 <- booleanFilter(`Bacterial Cells scatter|Yeast Cells scatter`)
node123<- gs_pop_add(selset.mix.iccmmmv,boolf2,
    parent="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone")

recompute(selset.yeast.iccmmmv)
recompute(selset.bact.iccmmmv)
recompute(selset.bact.iccams)
recompute(selset.mix.iccmmmv)

# use officer for slides -------------------------------------------------------
yeastfluoscatterslides <- read_pptx()
yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,layout = "Title Slide",
                                master = "Office Theme")
# layout_properties(yeastscatterslides,layout = "Title Slide")
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="Gating manual verification slides - SSC/BL1",
                              location=ph_location_type(type="ctrTitle"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="For check by Myrsini and Alexandra",
                              location=ph_location_type(type="subTitle"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, value = "slide 1", 
                              location = ph_location_type(type = "sldNum"))

yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,layout = "Section Header",
                                master = "Office Theme")

yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="Scatter & fluorescence -based secondary gating for yeast MMMV",
                              location=ph_location_type(type="title"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, value = "slide 2", 
                              location = ph_location_type(type = "sldNum"))
### yeast scatter & BL1 secondary ----------------------------------------------
for(i in 1:length(selset.yeast.iccmmmv)){
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+2), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvflscsecsing <- as.ggplot(ggcyto(selset.yeast.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Yeast Cells scatter alone") + 
                                     geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          theme_bw()+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccmmmvflscsecsing, 
                              location = ph_location_type(type = "body"))
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+2), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvflscsecsing <- as.ggplot(ggcyto(selset.yeast.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone") + 
                                     geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          theme_bw()+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccmmmvflscsecsing, 
                              location = ph_location_type(type = "body"))
  
}
## bacteria scatter & BL1 secondary MMMV ---------------------------------------
yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="Scatter and fluorescence-based secondary gating for bacteria MMMV",
                              location=ph_location_type(type="title"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = "With reference gate for yeast fluo/scatter", 
                              location = ph_location_type(type = "body"))

for(i in 1:length(selset.bact.iccmmmv)){
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluosingleb <- as.ggplot(ggcyto(selset.bact.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone") + geom_hex(bins=256) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSC)+
                                   geom_gate(polyGateICCbactSC,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccmmmvfluosingleb, 
                              location = ph_location_type(type = "body"))
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluosingleb <- as.ggplot(ggcyto(selset.bact.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone") + 
                                     geom_hex(bins=256) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSC)+
                                   geom_gate(polyGateICCbactSC,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccmmmvfluosingleb, 
                              location = ph_location_type(type = "body"))
  
}

## bacteria scatter and fluorescence AMS ---------------------------------------
yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="Scatter & fluoresence-based secondary gating for bacteria AMS",
                              location=ph_location_type(type="title"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = paste0("slide ",3+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.bact.iccams)){
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccamsscflsingleba <- as.ggplot(ggcyto(selset.bact.iccams[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone") + 
                                     geom_hex(bins=256) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSC)+
                                   geom_gate(polyGateICCbactSC,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccamsscflsingleba, 
                              location = ph_location_type(type = "body"))
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccamsscflsingleba <- as.ggplot(ggcyto(selset.bact.iccams[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                              subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone") +
                                     geom_hex(bins=256) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSC)+
                                   geom_gate(polyGateICCbactSC,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccamsscflsingleba, 
                              location = ph_location_type(type = "body"))
  
}

## KPME scatter and fluorescence MMMV ------------------------------------------
yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides,
                              value="Scatter and fluoresecence-based secondary gating for mix MMMV",
                              location=ph_location_type(type="title"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = paste0("slide ",5+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)+
                                               length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.mix.iccmmmv)){
  yeastfluoscatterslides <- add_slide(yeastfluoscatterslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)+
                                                 length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscfl1singleba <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone") +
                                       geom_hex(bins=256) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSC)+
                                   geom_gate(polyGateICCbactSC,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoscatterslides <- ph_with(yeastfluoscatterslides, 
                              value = piccmmmvscfl1singleba, 
                              location = ph_location_type(type = "body"))
  
}

print(yeastfluoscatterslides,target="gatinginspectionfluo_singlets.pptx")

```

###### ME in MMMV

Next, we inspect the secondary gating for ME in MMMV:

```{r sec_gating_ME, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of secondary gating results on ME in MMMV after filtering based upon the bacterial and yeast cell scatter gate.",cache=TRUE}
pICCMMVscBL1b <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone")
pICCMMVscBL1b + geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### ME in AMS

Next, we inspect the secondary gating for ME in AMS:

```{r sec_gating_ME_AMS, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of secondary gating results on ME in AMS after filtering based upon the bacterial and yeast cell scatter gate.",cache=TRUE, cache.lazy=FALSE}

pICCAMSscBL1b <- selset.bact.iccams[sample(1:length(selset.bact.iccams),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone")
pICCAMSscBL1b + geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()

```

###### Mix in MMMV

Finally, we inspect the secondary gating for KPME in MMV:

```{r sec_gating_KPME, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of secondary gating results on KPME in MMMV after filtering based upon the bacterial and yeast cell scatter gate.",cache=TRUE, cache.lazy=FALSE}
pICCMMVscBL1m <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone")
pICCMMVscBL1m + geom_hex(bins=256) + geom_gate(polyGateICCyeastSC) + 
          geom_gate(polyGateICCbactSC,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

##### Tertiairy gating ICC/DCC {.tabset .tabset-pills}

```{r iccdccgating_tertofficer,warning=FALSE,message=FALSE,cache=TRUE,cache.lazy=FALSE}
mixnodes <- gs_get_pop_paths(selset.mix.iccmmmv)
# use officer for slides -------------------------------------------------------
yeastfluoslides <- read_pptx()
yeastfluoslides <- add_slide(yeastfluoslides,layout = "Title Slide",
                                master = "Office Theme")
# layout_properties(yeastfluoslides,layout = "Title Slide")
yeastfluoslides <- ph_with(yeastfluoslides,
                              value="Gating manual verification slides - BL1/BL3",
                              location=ph_location_type(type="ctrTitle"))
yeastfluoslides <- ph_with(yeastfluoslides,
                              value="For check by Myrsini and Alexandra",
                              location=ph_location_type(type="subTitle"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoslides <- ph_with(yeastfluoslides, value = "slide 1", 
                              location = ph_location_type(type = "sldNum"))

yeastfluoslides <- add_slide(yeastfluoslides,layout = "Section Header",
                                master = "Office Theme")

yeastfluoslides <- ph_with(yeastfluoslides,
                              value="Fluoresence based tertiary ICC/DCC gating for yeast MMMV",
                              location=ph_location_type(type="title"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoslides <- ph_with(yeastfluoslides, value = "slide 2", 
                              location = ph_location_type(type = "sldNum"))
### yeast BL1/BL3 tertiary  ----------------------------------------------------
for(i in 1:length(selset.yeast.iccmmmv)){
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+2), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfltertsing <- as.ggplot(ggcyto(selset.yeast.iccmmmv[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
          subset="/Singlets/Yeast Cells scatter alone/Yeast Cells scatter") + 
                                     geom_hex(bins=512) + 
            geom_gate(polyGateDCC) + 
          geom_gate(polyGateICCyeast,colour="darkgreen") + 
          theme_bw()+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfltertsing, 
                              location = ph_location_type(type = "body"))
  
  
}
### bact MMMV BL1/BL3 tertiary  ----------------------------------------------------
yeastfluoslides <- add_slide(yeastfluoslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoslides <- ph_with(yeastfluoslides,
                              value="ICC/DCC tertiary gating for bacteria MMMV",
                              location=ph_location_type(type="title"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.bact.iccmmmv)){
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluotertsignb <- as.ggplot(ggcyto(selset.bact.iccmmmv[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone/Bacterial Cells scatter") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateDCCbact)+
                                   geom_gate(polyGateICCbact,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfluotertsignb, 
                              location = ph_location_type(type = "body"))
}

### bact AMS BL1/BL3 tertiary  ----------------------------------------------------
yeastfluoslides <- add_slide(yeastfluoslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoslides <- ph_with(yeastfluoslides,
                              value="ICC/DCC tertiary gating for ME in AMS",
                              location=ph_location_type(type="title"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.bact.iccams)){
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluotertsignba <- as.ggplot(ggcyto(selset.bact.iccams[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone/Bacterial Cells scatter") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateDCCbact)+
                                   geom_gate(polyGateICCbact,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfluotertsignba, 
                              location = ph_location_type(type = "body"))
}

### Mix MMV BL1/BL3 tertiary  ----------------------------------------------------
yeastfluoslides <- add_slide(yeastfluoslides,layout = "Section Header",
                                master = "Office Theme")
yeastfluoslides <- ph_with(yeastfluoslides,
                              value="ICC/DCC tertiary gating for Mix in MMV",
                              location=ph_location_type(type="title"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = "With reference gate for yeast and bacteria separately", 
                              location = ph_location_type(type = "body"))

for(i in 1:length(selset.mix.iccmmmv)){
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluotertsignmx <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
                                        subset=mixnodes[8]) + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateDCCbact) + 
                                   geom_gate(polyGateDCC,colour="firebrick1") +
                                   geom_gate(polyGateICCbact,colour="darkgreen") +
                                   geom_gate(polyGateICCyeast,colour="green") +
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfluotertsignmx, 
                              location = ph_location_type(type = "body"))
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluotertsignmxbo <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
                                        subset=mixnodes[6]) + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateDCCbact) + 
                                   geom_gate(polyGateDCC,colour="firebrick1") +
                                   geom_gate(polyGateICCbact,colour="darkgreen") +
                                   geom_gate(polyGateICCyeast,colour="green") +
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfluotertsignmxbo, 
                              location = ph_location_type(type = "body"))
  yeastfluoslides <- add_slide(yeastfluoslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluotertsignmxyo <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`BL1-H`,y=`BL3-H`),
                                        subset=mixnodes[7]) + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateDCCbact) + 
                                   geom_gate(polyGateDCC,colour="firebrick1") +
                                   geom_gate(polyGateICCbact,colour="darkgreen") +
                                   geom_gate(polyGateICCyeast,colour="green") +
                                   ggcyto_par_set(limits="instrument"))
  yeastfluoslides <- ph_with(yeastfluoslides, 
                              value = piccmmmvfluotertsignmxyo, 
                              location = ph_location_type(type = "body"))
}

print(yeastfluoslides,target="gatinginspectionfluo_tertiairy.pptx")
```


###### KP in MMMV

```{r iccdccgating_tert_y, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random yeast samples after primary and secondary gating."}
pICCMMVBL1BL3y <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets/Yeast Cells scatter alone/Yeast Cells scatter")
pICCMMVBL1BL3y + geom_hex(bins=256) + geom_gate(polyGateDCC) + 
          geom_gate(polyGateICCyeast,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```


###### ME in MMMV

```{r iccdccgating_tert_bm, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random ME in MMMV samples after primary and secondary gating."}
pICCMMVBL1BL3b <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets/Bacterial Cells scatter alone/Bacterial Cells scatter")
pICCMMVBL1BL3b + geom_hex(bins=256) + geom_gate(polyGateDCCbact) + 
          geom_gate(polyGateICCbact,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### ME in AMS

```{r iccdccgating_tert_ba, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random ME in AMS samples after primary and secondary gating."}
pICCMMVBL1BL3ba <- selset.bact.iccams[sample(1:length(selset.bact.iccams),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets/Bacterial Cells scatter alone/Bacterial Cells scatter")
pICCMMVBL1BL3ba + geom_hex(bins=256) + geom_gate(polyGateDCCbact) + 
          geom_gate(polyGateICCbact,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```


###### Mix in MMMV

Based upon the gating strategy, multiple hierarchical gates can be applied to 
the dataset:

```{r tertgatemixgh, warning=FALSE,message=FALSE,fig.cap="Gating strategy in case of tertiairy gating on the mix set."}
plot(selset.mix.iccmmmv,bool=TRUE)
```

First, the "OR" boolean gates were used to include all data:

```{r iccdccgating_tert_mx, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random mix in MMMV samples after primary and secondary gating. Bacterial ICC and DCC gates are shown in dark green and red, yeast ICC and DCC gates in light green and blue respectively."}
pICCMMVBL1BL3mx <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset=mixnodes[8])
pICCMMVBL1BL3mx + geom_hex(bins=256) + geom_gate(polyGateDCCbact) + 
          geom_gate(polyGateDCC,colour="blue") +
          geom_gate(polyGateICCbact,colour="darkgreen") +
          geom_gate(polyGateICCyeast,colour="green") +
          ggcyto_par_set(limits="instrument") + theme_bw()
```

Then, only the yeast cells were considered:

```{r iccdccgating_tert_mxyo, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random mix in MMMV samples after primary and secondary gating. Bacterial ICC and DCC gates are shown in dark green and red, yeast ICC and DCC gates in light green and blue respectively."}

pICCMMVBL1BL3mxyo <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset=mixnodes[7])
pICCMMVBL1BL3mxyo + geom_hex(bins=128) + geom_gate(polyGateDCCbact) + 
          geom_gate(polyGateDCC,colour="blue") +
          geom_gate(polyGateICCbact,colour="darkgreen") +
          geom_gate(polyGateICCyeast,colour="green") +
          ggcyto_par_set(limits="instrument") + theme_bw()
```

Next, only the bacterial cells were considered:

```{r iccdccgating_tert_mxbo, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random mix in MMMV samples after primary and secondary gating. Bacterial ICC and DCC gates are shown in dark green and red, yeast ICC and DCC gates in light green and blue respectively."}

pICCMMVBL1BL3mxbo <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset=mixnodes[6])
pICCMMVBL1BL3mxbo + geom_hex(bins=256) + geom_gate(polyGateDCCbact) + 
          geom_gate(polyGateDCC,colour="blue") +
          geom_gate(polyGateICCbact,colour="darkgreen") +
          geom_gate(polyGateICCyeast,colour="green") +
          ggcyto_par_set(limits="instrument") + theme_bw()

node7a <- gs_pop_add(selset.mix.iccmmmv,polyGateICCyeast,
                     parent="Yeast Cells scatter")
node7b <- gs_pop_add(selset.mix.iccmmmv,polyGateDCC,
                     parent="Yeast Cells scatter")

node7c <- gs_pop_add(selset.yeast.iccmmmv,polyGateICCyeast,
                     parent="Yeast Cells scatter")
node7d <- gs_pop_add(selset.yeast.iccmmmv,polyGateDCC,
                     parent="Yeast Cells scatter")

node8a <- gs_pop_add(selset.mix.iccmmmv,polyGateICCbact,
                     parent="Bacterial Cells scatter")
node8b <- gs_pop_add(selset.mix.iccmmmv,polyGateDCCbact,
                     parent="Bacterial Cells scatter")

node8c <- gs_pop_add(selset.bact.iccmmmv,polyGateICCbact,
                     parent="Bacterial Cells scatter")
node8d <- gs_pop_add(selset.bact.iccmmmv,polyGateDCCbact,
                     parent="Bacterial Cells scatter")

node8e <- gs_pop_add(selset.bact.iccams,polyGateICCbact,
                     parent="Bacterial Cells scatter")
node8f <- gs_pop_add(selset.bact.iccams,polyGateDCCbact,
                     parent="Bacterial Cells scatter")

boolf3 <- booleanFilter(`Intact Bacterial Cells fluo|Intact Yeast Cells`)
node1234<- gs_pop_add(selset.mix.iccmmmv,boolf3,
    parent="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone/Bacterial Cells scatter|Yeast Cells scatter")

recompute(selset.yeast.iccmmmv)
recompute(selset.bact.iccmmmv)
recompute(selset.bact.iccams)
recompute(selset.mix.iccmmmv)
```

##### Primary gating ICC/DCC {.tabset .tabset-pills}

In order to be more cautious about losing potentially relevant cell populations,
we also applied immediate gating on the singlets for ICC/DCC inference.

###### KP in MMMV

```{r iccdccgating_primyp, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random yeast samples after singlet gating."}
pICCMMVBL1BL3yp <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets")
pICCMMVBL1BL3yp + geom_hex(bins=256) + geom_gate(polyGateDCCprim) + 
          geom_gate(polyGateICCyeastprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### ME in MMMV

```{r iccdccgating_primmbm, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random ME in MMMV samples after singlet gating."}
pICCMMVBL1BL3yb <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets")
pICCMMVBL1BL3yb + geom_hex(bins=256) + geom_gate(polyGateDCCbactprim) + 
          geom_gate(polyGateICCbactprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### ME in AMS

```{r iccdccgating_primmba, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random ME in AMS samples after singlet gating."}
pICCMMVBL1BL3yba <- selset.bact.iccams[sample(1:length(selset.bact.iccams),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets")
pICCMMVBL1BL3yba + geom_hex(bins=256) + geom_gate(polyGateDCCbactprim) + 
          geom_gate(polyGateICCbactprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```


###### Mix in MMMV

Based upon the primary gating strategy, four subsets of the singlet gate can be
applied to the dataset.

```{r primgatemixgh, warning=FALSE,message=FALSE,fig.cap="Gating strategy in case of tertiairy gating on the mix set."}
node9a <- gs_pop_add(selset.mix.iccmmmv,polyGateICCbactprim,parent="Singlets")
node9b <- gs_pop_add(selset.mix.iccmmmv,polyGateDCCbactprim,parent="Singlets")
node9c <- gs_pop_add(selset.mix.iccmmmv,polyGateICCyeastprim,parent="Singlets")
node9d <- gs_pop_add(selset.mix.iccmmmv,polyGateDCCprim,parent="Singlets")
recompute(selset.mix.iccmmmv)
plot(selset.mix.iccmmmv,bool=TRUE)
# plot(selset.yeast.iccmmmv,bool=TRUE)
```

Due to the very strong overlap in yeast and bacteria gates it is very unlikely
that accurate concentrations can be found based upon primary gating for ICC/DCC 

```{r iccdccgating_primmmix, warning=FALSE,message=FALSE,fig.cap="ICC and DCC gates for 9 random Mix in MMMV samples after singlet gating."}
pICCMMVBL1BL3ymx <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`BL1-H`,y=`BL3-H`),
              subset="/Singlets")
pICCMMVBL1BL3ymx + geom_hex(bins=256) +
          geom_gate(polyGateDCCbactprim) + 
          geom_gate(polyGateDCCprim,colour="firebrick1") +
          geom_gate(polyGateICCbactprim,colour="darkgreen") +
          geom_gate(polyGateICCyeastprim,colour="green") +
          ggcyto_par_set(limits="instrument") + theme_bw()
```

##### Primary gating BL1/SSC, secondary ICC/DCC {.tabset .tabset-pills}

###### KP in MMMV

```{r fluorescencescprim_gating, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of primary gating results on KP after filtering based upon the singlets.",cache=TRUE, cache.lazy=FALSE}
recompute(selset.yeast.iccmmmv)
recompute(selset.bact.iccmmmv)
recompute(selset.bact.iccams)
recompute(selset.mix.iccmmmv)

node10a <- gs_pop_add(selset.yeast.iccmmmv,polyGateICCyeastSCprim,parent="/Singlets")
node10b <- gs_pop_add(selset.mix.iccmmmv,polyGateICCyeastSCprim,parent="/Singlets")

pICCMMVBL1SSCy <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets")
pICCMMVBL1SSCy + geom_hex(bins=256) + geom_gate(polyGateICCyeastSCprim) + 
          geom_gate(polyGateICCbactSCprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()

# pICCMMVBL1SSCyfsc <- selset.yeast.iccmmmv[sample(1:length(selset.yeast.iccmmmv),
#                                              9)] %>% 
#                       ggcyto(aes(x=`FSC-H`,y=`BL1-H`),
#               subset="/Singlets")
# 
# pICCMMVBL1SSCyfsc + geom_hex(bins=256) + 
#           ggcyto_par_set(limits="instrument") + theme_bw()

# use officer for slides -------------------------------------------------------
fluoscatterprimslides <- read_pptx()
fluoscatterprimslides <- add_slide(fluoscatterprimslides,layout = "Title Slide",
                                master = "Office Theme")
# layout_properties(yeastscatterslides,layout = "Title Slide")
fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="Gating manual verification slides - SSC/BL1 as primary",
                              location=ph_location_type(type="ctrTitle"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="For check by Myrsini and Alexandra",
                              location=ph_location_type(type="subTitle"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, value = "slide 1", 
                              location = ph_location_type(type = "sldNum"))

fluoscatterprimslides <- add_slide(fluoscatterprimslides,layout = "Section Header",
                                master = "Office Theme")

fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="Scatter & fluorescence -based primary gating for yeast MMMV",
                              location=ph_location_type(type="title"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, value = "slide 2", 
                              location = ph_location_type(type = "sldNum"))
### yeast scatter & BL1 primary ----------------------------------------------
for(i in 1:length(selset.yeast.iccmmmv)){
  fluoscatterprimslides <- add_slide(fluoscatterprimslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                                value = paste0("slide ",i+2), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvflscprimsing <- as.ggplot(ggcyto(selset.yeast.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets") + 
                                     geom_hex(bins=512) +
                                     geom_gate(polyGateICCyeastSCprim) + 
                                     geom_gate(polyGateICCbactSCprim,
                                               colour="darkgreen") + 
          theme_bw()+
                                   ggcyto_par_set(limits="instrument"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = piccmmmvflscprimsing, 
                              location = ph_location_type(type = "body"))
}
## bacteria scatter & BL1 primary MMMV ---------------------------------------
fluoscatterprimslides <- add_slide(fluoscatterprimslides,layout = "Section Header",
                                master = "Office Theme")
fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="Scatter and fluorescence-based primary gating for ME in MMMV",
                              location=ph_location_type(type="title"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = paste0("slide ",2+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = "With reference gate for yeast fluo/scatter", 
                              location = ph_location_type(type = "body"))
for(i in 1:length(selset.bact.iccmmmv)){
  fluoscatterprimslides <- add_slide(fluoscatterprimslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                                value = paste0("slide ",i+3+length(selset.yeast.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvfluosinglepb <- as.ggplot(ggcyto(selset.bact.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets") + geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSCprim)+
                                   geom_gate(polyGateICCbactSCprim,
                                             colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = piccmmmvfluosinglepb, 
                              location = ph_location_type(type = "body"))
}
## bacteria scatter and BL1 primary in AMS ---------------------------------------
fluoscatterprimslides <- add_slide(fluoscatterprimslides,layout = "Section Header",
                                master = "Office Theme")
fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="Scatter & fluoresence-based primary gating for ME in AMS",
                              location=ph_location_type(type="title"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = paste0("slide ",3+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.bact.iccams)){
  fluoscatterprimslides <- add_slide(fluoscatterprimslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)), 
                              location = ph_location_type(type = "sldNum"))
  piccamsscflsinglepba <- as.ggplot(ggcyto(selset.bact.iccams[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets") + 
                                     geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSCprim)+
                                   geom_gate(polyGateICCbactSCprim,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = piccamsscflsinglepba, 
                              location = ph_location_type(type = "body"))
}
# KPME scatter and fluorescence MMMV ------------------------------------------
fluoscatterprimslides <- add_slide(fluoscatterprimslides,layout = "Section Header",
                                master = "Office Theme")
fluoscatterprimslides <- ph_with(fluoscatterprimslides,
                              value="Scatter and fluoresecence-based primary gating for mix MMMV",
                              location=ph_location_type(type="title"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = paste0("slide ",5+length(selset.yeast.iccmmmv)+
                                               length(selset.bact.iccmmmv)+
                                               length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))

for(i in 1:length(selset.mix.iccmmmv)){
  fluoscatterprimslides <- add_slide(fluoscatterprimslides,
                                  layout = "Title and Content",
                                  master = "Office Theme")
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = format(Sys.Date()), 
                              location = ph_location_type(type = "dt"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                                value = paste0("slide ",i+4+
                                                 length(selset.yeast.iccmmmv)+
                                                 length(selset.bact.iccmmmv)+
                                                 length(selset.bact.iccams)), 
                              location = ph_location_type(type = "sldNum"))
  piccmmmvscfl1singlepm <- as.ggplot(ggcyto(selset.mix.iccmmmv[i],
                                        aes(x=`SSC-H`,y=`BL1-H`),
                                        subset="/Singlets/Bacterial Cells scatter alone|Yeast Cells scatter alone") +
                                       geom_hex(bins=512) + 
                                   theme_bw() + 
                                   geom_gate(polyGateICCyeastSCprim)+
                                   geom_gate(polyGateICCbactSCprim,colour="darkgreen")+
                                   ggcyto_par_set(limits="instrument"))
  fluoscatterprimslides <- ph_with(fluoscatterprimslides, 
                              value = piccmmmvscfl1singlepm, 
                              location = ph_location_type(type = "body"))
  
}

print(fluoscatterprimslides,target="gatinginspectionBL1SSCprimary_singlets.pptx")

```

###### ME in MMMV

```{r fluorescencescprim_gatingb, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of primary gating results on ME in MMMV after filtering based upon the singlets.",cache=TRUE, cache.lazy=FALSE}

pICCMMVscBLSC1b <- selset.bact.iccmmmv[sample(1:length(selset.bact.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets")
pICCMMVscBLSC1b + geom_hex(bins=256) + geom_gate(polyGateICCyeastSCprim) + 
          geom_gate(polyGateICCbactSCprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### ME in AMS

```{r fluorescencescprim_gatingba, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of primary gating results on ME in AMS after filtering based upon the singlets.",cache=TRUE, cache.lazy=FALSE}

pICCMMVscBLSC1ba <- selset.bact.iccams[sample(1:length(selset.bact.iccams),
                                             9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets")
pICCMMVscBLSC1ba + geom_hex(bins=256) + geom_gate(polyGateICCyeastSCprim) + 
          geom_gate(polyGateICCbactSCprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

###### Mix in MMMV

```{r fluorescencescprim_gatingmx, echo=TRUE, warning=FALSE,message=FALSE,cache=TRUE, fig.cap="Demonstration of primary gating results on Mix in MMMV after filtering based upon the singlets.",cache=TRUE, cache.lazy=FALSE}

pICCMMVscBLSC1mx <- selset.mix.iccmmmv[sample(1:length(selset.mix.iccmmmv),
                                             9)] %>% 
                      ggcyto(aes(x=`SSC-H`,y=`BL1-H`),
              subset="/Singlets")
pICCMMVscBLSC1mx + geom_hex(bins=256) + geom_gate(polyGateICCyeastSCprim) + 
          geom_gate(polyGateICCbactSCprim,colour="darkgreen") + 
          ggcyto_par_set(limits="instrument") + theme_bw()
```

### Results ICC/DCC

#### From tertiary gating

```{r ICCDCCtergat}
# iccmeta <- metadata_all %>% dplyr::filter(`Toanalyze?`=="Yes"&target=="ICC")
# selnamesICC <- c(sampleNames(selset.yeast.iccmmmv),sampleNames(selset.bact.iccmmmv),
#   sampleNames(selset.bact.iccams),sampleNames(selset.mix.iccmmmv))
# iccmeta.sel <- iccmeta[iccmeta$filenames%in%selnamesICC,]
# 
# openxlsx::write.xlsx(iccmeta.sel,file="ICCmetadata_for_dilutions.xlsx")
### filter correct dilutions ---------------------------------------------------
#### for yeast -----------------------------------------------------------------
correct_dilutions <- cordillstert %>% dplyr::filter(appropriate_dil_tert=="yes")
yeastcormd <- correct_dilutions %>% dplyr::filter(strain=="KP") %>% select(filenames,
                                                                           acquisitionvol,
                                                                           acquisitiondate,
                                                                           dilution,
                                                                           Replicateno)
yeastcormd$dilution_numeric <- 1L
yeastcormd$dilution_numeric[yeastcormd$dilution=="10min1"] <- 10L
yeastcormd$dilution_numeric[yeastcormd$dilution=="10min2"] <- 1e2L
yeastcormd$dilution_numeric[yeastcormd$dilution=="10min3"] <- 1e3L

yeastcormd$tpt <- gsub(".*_(t[0-9]).*","\\1",yeastcormd$filenames)

#### for ME in MMMV ------------------------------------------------------------
MEMMMVcormd <- correct_dilutions %>% 
                  dplyr::filter(strain=="ME"&Medium=="MMMV") %>% 
                  select(filenames,
                         acquisitionvol,
                         acquisitiondate,
                         dilution,
                         Replicateno)
MEMMMVcormd$dilution_numeric <- 1L
MEMMMVcormd$dilution_numeric[MEMMMVcormd$dilution=="10min1"] <- 10L
MEMMMVcormd$dilution_numeric[MEMMMVcormd$dilution=="10min2"] <- 1e2L
MEMMMVcormd$dilution_numeric[MEMMMVcormd$dilution=="10min3"] <- 1e3L

MEMMMVcormd$tpt <- gsub(".*_(t[0-9]).*","\\1",MEMMMVcormd$filenames)

#### for ME in AMS ------------------------------------------------------------
MEAMScormd <- correct_dilutions %>% 
                  dplyr::filter(strain=="ME"&Medium=="AMS") %>% 
                  select(filenames,
                         acquisitionvol,
                         acquisitiondate,
                         dilution,
                         Replicateno)
MEAMScormd$dilution_numeric <- 1L
MEAMScormd$dilution_numeric[MEAMScormd$dilution=="10min1"] <- 10L
MEAMScormd$dilution_numeric[MEAMScormd$dilution=="10min2"] <- 1e2L
MEAMScormd$dilution_numeric[MEAMScormd$dilution=="10min3"] <- 1e3L
MEAMScormd$dilution_numeric[MEAMScormd$dilution=="10min4"] <- 1e4L

MEAMScormd$tpt <- gsub(".*_(t[0-9]).*","\\1",MEAMScormd$filenames)

#### for Mix in MMMV -----------------------------------------------------------
MEMIXcormd <- correct_dilutions %>% 
                  dplyr::filter(strain=="KPME"&Medium=="MMMV") %>% 
                  select(filenames,
                         acquisitionvol,
                         acquisitiondate,
                         dilution,
                         Replicateno)
MEMIXcormd$dilution_numeric <- 1L
MEMIXcormd$dilution_numeric[MEMIXcormd$dilution=="10min1"] <- 10L
MEMIXcormd$dilution_numeric[MEMIXcormd$dilution=="10min2"] <- 1e2L
MEMIXcormd$dilution_numeric[MEMIXcormd$dilution=="10min3"] <- 1e3L
MEMIXcormd$dilution_numeric[MEMIXcormd$dilution=="10min4"] <- 1e4L
MEMIXcormd$tpt <- gsub(".*_(t[0-9]).*","\\1",MEMIXcormd$filenames)

### get nodes ------------------------------------------------------------------
yeastnodes <- gs_get_pop_paths(selset.yeast.iccmmmv)
bactMMMVnodes <- gs_get_pop_paths(selset.bact.iccmmmv)
bactAMSnodes <- gs_get_pop_paths(selset.bact.iccams)
mixnodes <- gs_get_pop_paths(selset.mix.iccmmmv)

### get stats ------------------------------------------------------------------

yeastpopstert <- gs_pop_get_count_fast(selset.yeast.iccmmmv[yeastcormd$filenames],
                                       subpopulations = c(yeastnodes[7],
                                                          yeastnodes[8]))

bacpopstert <- gs_pop_get_count_fast(selset.bact.iccmmmv[MEMMMVcormd$filenames],
                                       subpopulations = c(bactMMMVnodes[7],
                                                          bactMMMVnodes[8]))

bacapopstert <- gs_pop_get_count_fast(selset.bact.iccams[MEAMScormd$filenames],
                                       subpopulations = c(bactAMSnodes[7],
                                                          bactAMSnodes[8]))

mixpopstert <- gs_pop_get_count_fast(selset.mix.iccmmmv[MEMIXcormd$filenames],
                                       subpopulations = c(mixnodes[11],
                                                          mixnodes[12],
                                                          mixnodes[9],
                                                          mixnodes[10]))

yeastpopstert.md <- inner_join(yeastpopstert,yeastcormd,by=c("name"="filenames"))
yeastpopstert.md$strain <- "KP"
bacpopstert.md <- inner_join(bacpopstert,MEMMMVcormd,by=c("name"="filenames"))
bacpopstert.md$strain <- "ME_MMMV"
bacapopstert.md <- inner_join(bacapopstert,MEAMScormd,by=c("name"="filenames"))
bacapopstert.md$strain <- "ME_AMS"
mixpopstert.md <- inner_join(mixpopstert,MEMIXcormd,by=c("name"="filenames"))
mixpopstert.md$strain <- "ME_MMMV_mix"
mixpopstert.md$strain[grep("Yeast",mixpopstert.md$Population)]<-"KP_mix"

tertall <- rbind(yeastpopstert.md,bacpopstert.md,bacapopstert.md,mixpopstert.md)
tertall$membrane_integrity <- "Intact"
tertall$membrane_integrity[grep("Damaged",tertall$Population)]<-"Damaged"
tertall$tptnumeric <- as.numeric(gsub("t","",tertall$tpt))
tertall$tpth <- 0
tertall$tpth[tertall$tpt=="t1"]<-14.5
tertall$tpth[tertall$tpt=="t2"]<-19.5
tertall$tpth[tertall$tpt=="t3"]<-24
tertall$tpth[tertall$tpt=="t4"]<-38.5
tertall$tpth[tertall$tpt=="t5"]<-43.5
tertall$tpth[tertall$tpt=="t6"]<-48
tertall$tpth[tertall$tpt=="t7"]<-62.5
tertall$tpth[tertall$tpt=="t8"]<-67.5
tertall$tpth[tertall$tpt=="t9"]<-72


tertall$concentration <- tertall$Count/(as.numeric(tertall$acquisitionvol)/1e3L)*1e3L*tertall$dilution_numeric

wbtert <- openxlsx::createWorkbook()
openxlsx::addWorksheet(wbtert,sheetName = "Raw tertiary")
openxlsx::writeData(wbtert,sheet="Raw tertiary",tertall)

tertall.plot <- tertall %>% ggplot(aes(x=tpth,y=concentration,
                                       shape=membrane_integrity,fill=strain,
                                       color=strain))
tertall.plot + geom_point(size=3) + geom_smooth(se=TRUE) + scale_y_log10() + 
               facet_grid(membrane_integrity~strain,scales="free") + theme_bw() +
               ylab("Cell concentration (cells/mL)") + xlab("Time of cultivation (h)") +
               scale_shape_discrete(name="Membrane\nintegrity") +
               scale_color_discrete(name="Strain") +
               scale_fill_discrete(name="Strain")

tertall.sumd <- tertall %>% group_by(strain,membrane_integrity,tpt) %>%
                            summarise(avg_conc=mean(concentration),
                                      sd_conc=sd(concentration))
tertall.sumd$tptnumeric <- as.numeric(gsub("t","",tertall.sumd$tpt))

tertall.sumd$tpth <- 0
tertall.sumd$tpth[tertall.sumd$tpt=="t1"]<-14.5
tertall.sumd$tpth[tertall.sumd$tpt=="t2"]<-19.5
tertall.sumd$tpth[tertall.sumd$tpt=="t3"]<-24
tertall.sumd$tpth[tertall.sumd$tpt=="t4"]<-38.5
tertall.sumd$tpth[tertall.sumd$tpt=="t5"]<-43.5
tertall.sumd$tpth[tertall.sumd$tpt=="t6"]<-48
tertall.sumd$tpth[tertall.sumd$tpt=="t7"]<-62.5
tertall.sumd$tpth[tertall.sumd$tpt=="t8"]<-67.5
tertall.sumd$tpth[tertall.sumd$tpt=="t9"]<-72

openxlsx::addWorksheet(wbtert,sheetName = "Summarised tertiary")
openxlsx::writeData(wbtert,sheet="Summarised tertiary",tertall.sumd)
openxlsx::saveWorkbook(wbtert,file = "Tertiary_gating_concentrations.xlsx")

tertallsumd.plot <- tertall.sumd %>% ggplot(aes(x=tpth,y=avg_conc,
                                       shape=membrane_integrity,fill=strain,
                                       color=strain))



tertallsumd.plot + geom_point(size=3) + geom_errorbar(aes(ymin=avg_conc,
                                                          ymax=avg_conc+sd_conc)) +
               geom_line() + scale_y_log10() +
               facet_grid(membrane_integrity~strain,scales="free") + theme_bw() +
               ylab("Cell concentration (cells/mL)") + xlab("Time of cultivation (h)") +
               scale_shape_discrete(name="Membrane\nintegrity") +
               scale_color_discrete(name="Strain") +
               scale_fill_discrete(name="Strain")

```


## Cell size and biovolume over time

#### Build size model

##### Extract bead information - conventional beads

```{r sizemodbuild, echo=FALSE,warning=FALSE}
# Read bead FCS files ----------------------------------------------------------
beadsfs <- read.flowSet(path="source_data/size_beads/",pattern="*.fcs",
                        emptyValue = FALSE)
# Extract voltages for comparison ----------------------------------------------
# beadsfs[[1]]@description$`$P11N` # FSC-H
# beadsfs[[1]]@description$`$P12N` # SSC-H
# beadsfs[[1]]@description$`#TR1` # fluorescence threshold on BL1
fsch_voltage <- as.numeric(unique(fsApply(beadsfs,
                                          function(x)x@description$`$P11V`)))
ssch_voltage <- as.numeric(unique(fsApply(beadsfs,
                                          function(x)x@description$`$P12V`)))
thresholdbeads <- unique(fsApply(beadsfs,function(x)x@description$`#TR1`))

# Transform FCS data -----------------------------------------------------------
chnls <- colnames(beadsfs)[2:28]
transList <- transformerList(chnls,trans.obj)
gatingsetsizebeads <- GatingSet(beadsfs)
gatingsetsizebeads <- transform(gatingsetsizebeads, transList)
beadsfs_transformed <- cytoset_to_flowSet(gs_pop_get_data(gatingsetsizebeads))

# Gate definition for the beads ------------------------------------------------

sqrcut02um <- matrix(c(5.850,5.850,9.350,9.350,
                       7.500,8.475,8.475,7.500),
                      ncol=2, nrow=4)
colnames(sqrcut02um) <- c("FSC-H","SSC-H")
polyGate_02umSC <- polygonGate(.gate=sqrcut02um, filterId = "200nm")

sqrcut05um <- matrix(c(6.750,6.750,9.750,9.750,
                       9.650,10.25,10.25,9.650),
                      ncol=2, nrow=4)
colnames(sqrcut05um) <- c("FSC-H","SSC-H")
polyGate_05umSC <- polygonGate(.gate=sqrcut05um, filterId = "500nm")

sqrcut1um <- matrix(c(10.15,10.15,11.25,11.25,
                      11.00,12.50,12.50,11.00),
                      ncol=2, nrow=4)
colnames(sqrcut1um) <- c("FSC-H","SSC-H")
polyGate_1umSC <- polygonGate(.gate=sqrcut1um, filterId = "1000nm")

# Visualize gates --------------------------------------------------------------
pbeads <- beadsfs_transformed %>% ggcyto(aes(x=`FSC-H`,y=`SSC-H`))
pbeads + geom_hex(bins=256) + theme_bw() + labs_cyto("marker") +
         geom_gate(polyGate_02umSC) + 
         geom_gate(polyGate_05umSC,colour="blue") +
         geom_gate(polyGate_1umSC,colour="green")
# Subset to beads, combine and merge -------------------------------------------
names1um <- grep("1um",sampleNames(beadsfs),value=TRUE)
names500nm <- grep("0.5um",sampleNames(beadsfs),value=TRUE)
names200nm <- grep("0.2um",sampleNames(beadsfs),value=TRUE)
fs1um <- Subset(beadsfs_transformed[names1um],polyGate_1umSC)
fs500nm <- Subset(beadsfs_transformed[names500nm],polyGate_05umSC)
fs200nm <- Subset(beadsfs_transformed[names200nm],polyGate_02umSC)

allbeads <- rbind2(fs200nm,rbind2(fs500nm,fs1um))
allbeads.merged <- FCS_pool(allbeads,"*")

# Create filterlist
filterslmerge <- filters(list(polyGate_02umSC,
                              polyGate_05umSC,
                              polyGate_1umSC))
flistmerge <- list(filterslmerge)
names(flistmerge) <- flowCore::sampleNames(allbeads.merged)

pdfbeads <- phenoData(allbeads)
pdfbeads$beadsize <- c(rep(0.2,3),rep(0.5,3),rep(1,3))
```

##### Extract bead information - creative beads

```{r sizemodbuild, echo=FALSE,warning=FALSE}
# Read bead FCS files ----------------------------------------------------------
beadsfs_crea <- read.flowSet(path="source_data/size_beads/josefien/",pattern="*.fcs",
                        emptyValue = FALSE)
# Extract voltages for comparison ----------------------------------------------
# beadsfs_crea[[1]]@description$`$P11N` # FSC-H
# beadsfs_crea[[1]]@description$`$P12N` # SSC-H
# beadsfs_crea[[1]]@description$`#TR1` # fluorescence threshold on BL1
fsch_voltage_crea <- as.numeric(unique(fsApply(beadsfs_crea,
                                          function(x)x@description$`$P11V`)))
ssch_voltage_crea <- as.numeric(unique(fsApply(beadsfs_crea,
                                          function(x)x@description$`$P12V`)))
thresholdbeads_crea <- unique(fsApply(beadsfs_crea,function(x)x@description$`#TR1`))

# Transform FCS data -----------------------------------------------------------
chnls <- colnames(beadsfs_crea)[2:28]
transList <- transformerList(chnls,trans.obj)
gatingsetsizebeads_crea <- GatingSet(beadsfs_crea)
gatingsetsizebeads_crea <- transform(gatingsetsizebeads_crea, transList)
beadsfs_transformed_crea <- cytoset_to_flowSet(gs_pop_get_data(gatingsetsizebeads_crea))

# Gate definition for the beads ------------------------------------------------

# sqrcut02um <- matrix(c(5.850,5.850,9.350,9.350,
#                        7.500,8.475,8.475,7.500),
#                       ncol=2, nrow=4)
# colnames(sqrcut02um) <- c("FSC-H","SSC-H")
# polyGate_02umSC <- polygonGate(.gate=sqrcut02um, filterId = "200nm")


sqrcutallbeads <- matrix(c(5.00,5.00,12.50,12.50,
                           5.00,12.5,12.50,5.00),
                      ncol=2, nrow=4)
colnames(sqrcutallbeads) <- c("FSC-H","SSC-H")
polyGate_allbeadsSC <- polygonGate(.gate=sqrcutallbeads, filterId = "beadsSC")

sqrcut05um <- matrix(c(7.750,7.750,8.750,8.750,
                       6.450,7.300,7.300,6.450),
                      ncol=2, nrow=4)
colnames(sqrcut05um) <- c("FSC-H","SSC-H")
polyGate_05umSC <- polygonGate(.gate=sqrcut05um, filterId = "500nm")

sqrcut1um <- matrix(c(8.15,8.15,9.50,9.50,
                      7.50,8.25,8.25,7.50),
                      ncol=2, nrow=4)
colnames(sqrcut1um) <- c("FSC-H","SSC-H")
polyGate_1umSC <- polygonGate(.gate=sqrcut1um, filterId = "1000nm")

sqrcut2umAttuneFluoL1 <- matrix(c(10.9,10.9,11.15,11.15,
                                  6.50,7.50,7.50,6.50),
                      ncol=2, nrow=4)
colnames(sqrcut2umAttuneFluoL1) <- c("FSC-H","BL1-H")
polyGate_AttuneFluoL1 <- polygonGate(.gate=sqrcut2umAttuneFluoL1,
                                     filterId = "2400nmFA")

sqrcut2umAttuneSCL1 <- matrix(c(10.9,10.9,11.15,11.15,
                                10.0,11.25,11.25,10.0),
                      ncol=2, nrow=4)
colnames(sqrcut2umAttuneSCL1) <- c("FSC-H","SSC-H")
polyGate_AttuneSCL1 <- polygonGate(.gate=sqrcut2umAttuneSCL1,
                                     filterId = "2400nmSC")

sqrcut3umAttuneFluoL1 <- matrix(c(11.15,11.15,11.35,11.35,
                                  6.50,13.50,13.50,6.50),
                      ncol=2, nrow=4)
colnames(sqrcut3umAttuneFluoL1) <- c("FSC-H","BL1-H")
polyGate_AttuneFluoL234 <- polygonGate(.gate=sqrcut3umAttuneFluoL1,
                                     filterId = "3200nmFA")

 

nodebeadscrea1 <- gs_pop_add(gatingsetsizebeads_crea,polyGate_allbeadsSC)
nodebeadscrea2 <- gs_pop_add(gatingsetsizebeads_crea,
                             polyGate_05umSC,
                             parent="beadsSC")
nodebeadscrea3 <- gs_pop_add(gatingsetsizebeads_crea,
                             polyGate_1umSC,
                             parent="beadsSC")
nodebeadscrea4 <- gs_pop_add(gatingsetsizebeads_crea,
                             polyGate_AttuneFluoL1,
                             parent="beadsSC")
nodebeadscrea5 <- gs_pop_add(gatingsetsizebeads_crea,
                             polyGate_AttuneSCL1,
                             parent="beadsSC")
nodebeadscrea6 <- gs_pop_add(gatingsetsizebeads_crea,
                             polyGate_AttuneFluoL234,
                             parent="beadsSC")

plot(gatingsetsizebeads_crea)
recompute(gatingsetsizebeads_crea)

# Visualize gates --------------------------------------------------------------
selsamps <- sampleNames(beadsfs_transformed_crea)[c(3,
                                        5:length(sampleNames(beadsfs_transformed_crea)))]

pbeads <- beadsfs_transformed_crea[selsamps] %>% ggcyto(aes(x=`FSC-H`,y=`SSC-H`))
pbeads + geom_hex(bins=512) + theme_bw() + labs_cyto("marker") +
         geom_gate(polyGate_allbeadsSC) +
         geom_gate(polyGate_05umSC,colour="blue") +
         geom_gate(polyGate_1umSC,colour="green")

pbeads_gs <- gatingsetsizebeads_crea[selsamps[2]] %>%
  ggcyto(aes(x=`FSC-H`,y=`SSC-H`),subset="beadsSC")
pbeads_gs + geom_hex(bins=256) + theme_bw() + labs_cyto("marker") +
        ggcyto_par_set(limits="instrument")+
         geom_gate(polyGate_05umSC,colour="blue") +
         geom_gate(polyGate_1umSC,colour="green") + 
         geom_gate(polyGate_AttuneSCL1)

fsApply(beadsfs_transformed_crea,function(x)x@description$`$P11V`)
fsApply(beadsfs_transformed_crea,function(x)x@description$`$P12V`)

pbeadsfluo <- gatingsetsizebeads_crea[selsamps[4]] %>% ggcyto(aes(x=`FSC-H`,y=`BL1-H`),
                                                              subset="beadsSC")
pbeadsfluo + geom_hex(bins=512) + theme_bw() + 
  labs_cyto("marker") + geom_gate(polyGate_AttuneFluoL1) + 
  geom_gate(polyGate_AttuneFluoL234,colour="green")

pbeadsfluoA <- gatingsetsizebeads_crea[selsamps[4]] %>% ggcyto(aes(x=`FSC-A`,y=`BL1-H`),
                                                              subset="beadsSC")
pbeadsfluoA + geom_hex(bins=512) + theme_bw()

pbeadsfluossc <- beadsfs_transformed_crea[selsamps[4]] %>% ggcyto(aes(x=`SSC-H`,y=`BL1-H`))
pbeadsfluossc + geom_hex(bins=512) + theme_bw() 

# Subset to beads, combine and merge -------------------------------------------
fscrea500nm <- Subset(beadsfs_transformed_crea[selsamps[1]],polyGate_05umSC)
fscrea1um <- Subset(beadsfs_transformed_crea[selsamps[2]],polyGate_1umSC)
fscrea2400nm <- Subset(beadsfs_transformed_crea[selsamps[4]],polyGate_AttuneSCL1)


allbeads_Crea <- rbind2(fscrea500nm,rbind2(fscrea1um,fscrea2400nm))
allbeads_crea.merged <- FCS_pool(allbeads_Crea,"*")

# Create filterlist
filterslmerge <- filters(list(polyGate_05umSC,
                              polyGate_1umSC,
                              polyGate_AttuneSCL1))
flistmerge <- list(filterslmerge)
names(flistmerge) <- flowCore::sampleNames(allbeads_crea.merged)

pdfbeads <- phenoData(allbeads_Crea)
pdfbeads$beadsize <- c(0.5,1,2.4)
```


#### Size model building and applying

##### Building

```{r buildsizemod}
# only for the yeast pop
# plot(selset.yeast.iccmmmv, bool=TRUE)
primyeastfs.sing <- cytoset_to_flowSet(gs_pop_get_data(selset.yeast.iccmmmv,
                                    y=yeastnodes[9]))
tertyeastfs.sing <- cytoset_to_flowSet(gs_pop_get_data(selset.yeast.iccmmmv,
                                    y=yeastnodes[6]))
tertyeastfs.sing.icc <- cytoset_to_flowSet(gs_pop_get_data(selset.yeast.iccmmmv,
                                    y=yeastnodes[7]))

# checking if flowSets correspond to settings used for the beads ---------------
fsch_voltage.icc <- as.numeric(unique(fsApply(tertyeastfs.sing.icc,
                                          function(x)x@description$`$P11V`)))
ssch_voltage.icc <- as.numeric(unique(fsApply(tertyeastfs.sing.icc,
                                          function(x)x@description$`$P12V`)))
thresholdbeads.icc <- unique(fsApply(tertyeastfs.sing.icc,
                                     function(x)x@description$`#TR1`))




fsch_voltage.sypro <- as.numeric(unique(fsApply(hierarchfsSYPRO.clean.atd,
                                          function(x)x@description$`$P11V`)))
ssch_voltage.sypro <- as.numeric(unique(fsApply(hierarchfsSYPRO.clean.atd,
                                          function(x)x@description$`$P12V`)))
thresholdbeads.sypro <- unique(fsApply(hierarchfsSYPRO.clean.atd,
                                     function(x)x@description$`#TR1`))
thresholdbeads.sypro2 <- unique(fsApply(hierarchfsSYPRO.clean.atd,
                                     function(x)x@description$`#TR2`))

fsch_voltage.bodipy <- as.numeric(unique(fsApply(hierarchfsBODIPYKP.clean.atd,
                                          function(x)x@description$`$P11V`)))
ssch_voltage.bodipy <- as.numeric(unique(fsApply(hierarchfsBODIPYKP.clean.atd,
                                          function(x)x@description$`$P12V`)))
thresholdbeads.bodipy <- unique(fsApply(hierarchfsBODIPYKP.clean.atd,
                                     function(x)x@description$`#TR1`))
thresholdbeads.bodipy2 <- unique(fsApply(hierarchfsBODIPYKP.clean.atd,
                                     function(x)x@description$`#TR2`))
# Run (abridged version of) KytoSize -------------------------------------------
library(gam)
# sizeresicc <- KytoSize(fsetICC.iccgate,
#                        fcs_mp = allbeads.merged,
#                        flist=flistmerge,
#                        bead_selection=c(0.2,0.5,1),
#                        param=c("FSC-H","SSC-H"),
#                        format="summary")
## General parameters ----------------------------------------------------------
fcs_mp  <- allbeads_crea.merged
flist   <- flistmerge
p_train <- 0.75
bead_selection <- c(0.5,1,2.4)
param <- c("FSC-H","SSC-H")
format <- "summary"
plot <- TRUE
sample_size <- 1.1e3L
return_models <- TRUE
ref_model <- NULL
size_model <- NULL

# Step 1) Denoise the data
fcs_mp <- fcs_mp[, param]

fcs_mp_1 <-
  run_quiet(FCS_resample(Subset(fcs_mp, flist[[1]][1][[1]]), sample=278))
fcs_mp_2 <-
  run_quiet(FCS_resample(Subset(fcs_mp, flist[[1]][2][[1]]), sample=963))
fcs_mp_3 <-
  run_quiet(FCS_resample(Subset(fcs_mp, flist[[1]][3][[1]]), sample=5e3))

# Step 2: make dataset to train model
ssc_mp <-
  data.table(
    Size = c(
      rep(0.5, nrow(fcs_mp_1[[1]]@exprs)),
      rep(1, nrow(fcs_mp_2[[1]]@exprs)),
      rep(2.4, nrow(fcs_mp_3[[1]]@exprs))
    ),
    param_1 = c(
      fcs_mp_1[[1]]@exprs[, param[1]],
      fcs_mp_2[[1]]@exprs[, param[1]],
      fcs_mp_3[[1]]@exprs[, param[1]]
    ),
    param_2 = c(
      fcs_mp_1[[1]]@exprs[, param[2]],
      fcs_mp_2[[1]]@exprs[, param[2]],
      fcs_mp_3[[1]]@exprs[, param[2]]
    )
  )
# Filter out relevant bead sets
ssc_mp <- ssc_mp[ssc_mp$Size %in% bead_selection,]

# Step 3: Set model parameters
fitControl <- caret::trainControl(## 10-fold CV
  method = "repeatedcv",
  number = 10,
  ## repeated ten times
  repeats = 3)

# Step 4: Create data partitions
trainIndex <-
  caret::createDataPartition(ssc_mp$Size, p = p_train)
train_data <- ssc_mp[trainIndex$Resample1,]
test_data <- ssc_mp[-trainIndex$Resample1,]
train_data_BV <- train_data %>%
  mutate(Biovolume = pi * ((Size) ^ 3) / 6)
test_data_BV <- test_data %>%
  mutate(Biovolume = pi * ((Size) ^ 3) / 6)

# Step 5: Train Random Forest classifier on training set
tunegrid <- base::expand.grid(df = 3)
KYTOmodel_micropart <-
  caret::train(
    Size ~ param_1 + param_2,
    data = train_data,
    method = "gamSpline",
    metric = "RMSE",
    tuneGrid = tunegrid,
    trControl = fitControl
  )
KYTOmodel_micropart_BV <-
  caret::train(
    Biovolume ~ param_1 + param_2,
    data = train_data_BV,
    method = "gamSpline",
    metric = "RMSE",
    tuneGrid = tunegrid,
    trControl = fitControl
  )
print(KYTOmodel_micropart)
print(KYTOmodel_micropart_BV)
saveRDS(KYTOmodel_micropart, file = "./Results/SizeModnew.Rds")
saveRDS(KYTOmodel_micropart_BV, file = "./Results/VolumeModnew.Rds")

# For predictions
RF_pred <-
  predict.train(KYTOmodel_micropart, newdata = test_data)
RF_pred <- data.table(Predicted_size = RF_pred, test_data)
RF_pred_BV <-
  predict.train(KYTOmodel_micropart_BV, newdata = test_data_BV)
RF_pred_BV <-
  data.table(Predicted_biovolume = RF_pred_BV, test_data_BV)
if (plot == TRUE) {
  p1 <- ggplot2::ggplot(RF_pred, aes(x = Size, y = Predicted_size)) +
    ggplot2::geom_point(shape = 21,
      size = 3,
      fill = "#ffa401") +
    ggplot2::theme_bw() +
    ggplot2::geom_smooth(method = "lm",
      col = "black",
      linetype = 2) +
    ggplot2::geom_abline(
      slope = 1,
      col = "darkgreen",
      linetype = 2,
      size = 1.2
    ) +
    ggplot2::xlim(-0.1, max(bead_selection) + 0.2) +
    ggplot2::ylim(-0.1, max(bead_selection) + 0.2) +
    ggplot2::ggtitle("Model performance on test set") +
    ylab(expression(Predicted ~ size ~ (mu * m))) +
    xlab(expression(Size ~ (mu * m))) +
    ggplot2::annotate("text", x = 0.5, y = 2, label=
             bquote(R^{2}==.(signif(KYTOmodel_micropart$results$Rsquared, 4))))
  
  p2 <-
    ggplot2::ggplot(RF_pred_BV, aes(x = Biovolume, y = Predicted_biovolume)) +
    ggplot2::geom_point(shape = 21,
      size = 3,
      fill = "#ffa401") +
    ggplot2::theme_bw() +
    ggplot2::geom_smooth(method = "lm",
      col = "black",
      linetype = 2) +
    ggplot2::geom_abline(
      slope = 1,
      col = "darkgreen",
      linetype = 2,
      size = 1.2
    ) +
    ggplot2::xlim(-0.1, max(pi * (bead_selection ^ 3) / 6) + 0.2) +
    ggplot2::ylim(-0.1, max(pi * (bead_selection ^ 3) / 6) + 0.2) +
    ggplot2::ggtitle("Model performance on test set") +
    ylab(expression(Predicted ~ (bio) * volume ~ (mu * m ^ 3)))  +
    xlab(expression(Volume ~ (mu * m ^ 3)))+
    ggplot2::annotate("text", x = 0.5, y = 6, label=
             bquote(R^{2}==.(signif(KYTOmodel_micropart_BV$results$Rsquared, 4))))
  
  print(cowplot::plot_grid(p1, p2, align = "hv"))
}

```

##### Apply to ICC data

```{r resicc}
## For the ICC flowSet ---------------------------------------------------------
fcs_x   <- tertyeastfs.sing.icc
# filter out params of interest
fcs_x <- fcs_x[, param]
# actual size inferences
results_sizing.icc <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <- c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart, newdata = x))
})
results_sizing_BV.icc <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <-   c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart_BV, newdata = x))
})
# we calculated the results in a summary format 
results_sizing.icc.summary <- data.table(
  Sample_names = names(results_sizing.icc),
  med_value = unlist(lapply(
    results_sizing.icc,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing.icc,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing.icc,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing.icc,
    FUN = function(x)
      length(x$V1)
  ))
)
results_sizing_BV.icc.summary <- data.table(
  Sample_names = names(results_sizing_BV.icc),
  med_value = unlist(lapply(
    results_sizing_BV.icc,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing_BV.icc,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing_BV.icc,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing_BV.icc,
    FUN = function(x)
      length(x$V1)
  ))
)
openxlsx::addWorksheet(reswb,sheetName = "ICC_diameter")
openxlsx::writeData(reswb,sheet="ICC_diameter",x = results_sizing.icc.summary)
openxlsx::addWorksheet(reswb,sheetName = "ICC_volume")
openxlsx::writeData(reswb,sheet="ICC_volume",x = results_sizing_BV.icc.summary)
sizeicc.md <- dplyr::left_join(results_sizing.icc.summary,
                               iccmeta.sel,
                               by=c("Sample_names"="filenames"))
sizeicc.md$timepoint <- gsub(".*(t[0-9]).*","\\1",sizeicc.md$Sample_names)
sizeicc.md %>% dplyr::filter(ncells>500) %>% group_by(timepoint,dilution) %>% 
               summarise(avgmedsize=mean(med_value),
                         sdmedsize=sd(med_value)) %>%
               ggplot(.,aes(x=timepoint,y=avgmedsize,color=dilution)) +
               geom_point() + geom_smooth(se=FALSE) + 
               geom_errorbar(aes(ymin=avgmedsize-sdmedsize,
                                 ymax=avgmedsize+sdmedsize)) +
               theme_bw() + xlab("Incubation timepoint") + 
               ylab("Average of the median cell size across biological replicates (µm, n=4)")
openxlsx::saveWorkbook(reswb,file = "results/FcM_results.xlsx",overwrite = TRUE)
```

##### Apply to SYPRO data

```{r ressypro}
## For the SYPRO flowSet ---------------------------------------------------------
fcs_x   <- hierarchfsSYPRO.clean.atd
# filter out params of interest
fcs_x <- fcs_x[, param]
# actual size inferences
results_sizing.sypro <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <- c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart, newdata = x))
})
results_sizing_BV.sypro <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <-   c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart_BV, newdata = x))
})
# we calculated the results in a summary format 
results_sizing.sypro.summary <- data.table(
  Sample_names = names(results_sizing.sypro),
  med_value = unlist(lapply(
    results_sizing.sypro,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing.sypro,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing.sypro,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing.sypro,
    FUN = function(x)
      length(x$V1)
  ))
)
results_sizing_BV.sypro.summary <- data.table(
  Sample_names = names(results_sizing_BV.sypro),
  med_value = unlist(lapply(
    results_sizing_BV.sypro,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing_BV.sypro,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing_BV.sypro,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing_BV.sypro,
    FUN = function(x)
      length(x$V1)
  ))
)
openxlsx::addWorksheet(reswb,sheetName = "SYPRO_diameter")
openxlsx::writeData(reswb,sheet="SYPRO_diameter",x = results_sizing.sypro.summary)
openxlsx::addWorksheet(reswb,sheetName = "SYPRO_volume")
openxlsx::writeData(reswb,sheet="SYPRO_volume",x = results_sizing_BV.sypro.summary)

openxlsx::saveWorkbook(reswb,file = "results/FcM_results.xlsx",overwrite = TRUE)
```

##### Apply to BODIPY data

```{r resbodipy}
## For the BODIPY flowSet ---------------------------------------------------------
fcs_x   <- hierarchfsBODIPYKP.clean.atd
# filter out params of interest
fcs_x <- fcs_x[, param]
# actual size inferences
results_sizing.bodipy <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <- c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart, newdata = x))
})
results_sizing_BV.bodipy <- fsApply(fcs_x, use.exprs = TRUE, function(x) {
  x <-
    x[, param[1:2], drop = FALSE]
  colnames(x) <-   c("param_1", "param_2")
  RF_pred <-
    data.table(predict.train(KYTOmodel_micropart_BV, newdata = x))
})
# we calculated the results in a summary format 
results_sizing.bodipy.summary <- data.table(
  Sample_names = names(results_sizing.bodipy),
  med_value = unlist(lapply(
    results_sizing.bodipy,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing.bodipy,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing.bodipy,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing.bodipy,
    FUN = function(x)
      length(x$V1)
  ))
)
results_sizing_BV.bodipy.summary <- data.table(
  Sample_names = names(results_sizing_BV.bodipy),
  med_value = unlist(lapply(
    results_sizing_BV.bodipy,
    FUN = function(x)
      median(x$V1)
  )),
  q25 = unlist(lapply(
    results_sizing_BV.bodipy,
    FUN = function(x)
      quantile(x$V1, probs = 0.25)
  )),
  q75 = unlist(lapply(
    results_sizing_BV.bodipy,
    FUN = function(x)
      quantile(x$V1, probs = 0.75)
  )),
  ncells = unlist(lapply(
    results_sizing_BV.bodipy,
    FUN = function(x)
      length(x$V1)
  ))
)
openxlsx::addWorksheet(reswb,sheetName = "BODIPY_diameter")
openxlsx::writeData(reswb,sheet="BODIPY_diameter",x = results_sizing.bodipy.summary)
openxlsx::addWorksheet(reswb,sheetName = "BODIPY_volume")
openxlsx::writeData(reswb,sheet="BODIPY_volume",x = results_sizing_BV.bodipy.summary)

openxlsx::saveWorkbook(reswb,file = "Results/FcM_results.xlsx",overwrite = TRUE)
```

## Co-culture composition over time

### Model-free (gated) approach

### Using machine learning

## Protein and nucleic acid 

### Gating strategy

```{r syprogatesandpreprocessing, echo=FALSE,warning=FALSE,message=FALSE,cache.lazy=FALSE}
# SYPRO dataset ----------------------------------------------------------------
## ETL -------------------------------------------------------------------------
mddf.toanalyze.SYPRO.MMMV.KP <- mddf.toanalyze %>%
  dplyr::filter(target == "PROTEIN" &
                  Medium == "MMMV" &
                  strain == "KP")

mddf.toanalyze.SYPRO.MMMV.KP$timepoint <- gsub(".*(t[0-9]).fcs","\\1",
                                      mddf.toanalyze.SYPRO.MMMV.KP$filenames)

flowsetSYPROKP <- allfs.orig[mddf.toanalyze.SYPRO.MMMV.KP$filenames]

flowsetSYPROKP.clean <- FCS_clean(flowsetSYPROKP,
                                  param = c("BL2-H", "RL1-H",
                                            "SSC-H", "FSC-H"))

chnls <- colnames(flowsetSYPROKP)[2:28]
transList <- transformerList(chnls,trans.obj)
gatingsetSYPROKP <- GatingSet(flowsetSYPROKP)
gatingsetSYPROKP <- transform(gatingsetSYPROKP, transList)
flowsetSYPROKP_transformed <- cytoset_to_flowSet(gs_pop_get_data(gatingsetSYPROKP))

gatingsetSYPROKP.hier <- GatingSet(flowsetSYPROKP)
gatingsetSYPROKP.hier <- transform(gatingsetSYPROKP.hier, transList)


gatingsetSYPROKP.hier.clean <- GatingSet(flowsetSYPROKP.clean)
gatingsetSYPROKP.hier.clean <- transform(gatingsetSYPROKP.hier.clean, transList)

## Gating strategy -------------------------------------------------------------
sqrcutSYPROSYTO<- matrix(c(5, 12, 15.0,5,
                           5, 5, 14.5,14.5),
     ncol = 2,
     nrow = 4)
colnames(sqrcutSYPROSYTO) <- c("BL2-H", "RL1-H")
polyGateSYPROSYTO <- polygonGate(.gate = sqrcutSYPROSYTO, filterId = "Dual positive")

sqrcutSYPROSSC <- matrix(c(4.6, 4.5, 4.50, 15.0, 15.0,
                           6.1, 6.75, 12.5, 12.5, 6.1),
     ncol = 2,
     nrow = 5)
colnames(sqrcutSYPROSSC) <- c("BL2-H", "SSC-H")
polyGateSYPROSSC <- polygonGate(.gate = sqrcutSYPROSSC, filterId = "SYPRO+")

nodes1 <- gs_pop_add(gatingsetSYPROKP.hier,polyGateSYPROSSC)
nodes2 <- gs_pop_add(gatingsetSYPROKP.hier,polyGateSYPROSYTO,parent="SYPRO+")
recompute(gatingsetSYPROKP.hier)
plot(gatingsetSYPROKP.hier)

nodes1.clean <- gs_pop_add(gatingsetSYPROKP.hier.clean, polyGateSYPROSSC)
nodes2.clean <- gs_pop_add(gatingsetSYPROKP.hier.clean,
                           polyGateSYPROSYTO, parent="SYPRO+")
recompute(gatingsetSYPROKP.hier.clean)

pSYPROKPSYTOgates <- ggcyto(gatingsetSYPROKP.hier,
                            aes(x="RL1-H",y="BL2-H"),subset="SYPRO+")
pSYPROKPSYTOgates + geom_hex(bins=512) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateSYPROSYTO,colour="orangered") 
# pdf("Gating_hierarchy_SYPRO.pdf")
# lapply(gatingsetSYPRO.hier,function(x)autoplot(x,bins=256)+theme_bw())
# dev.off()

# for(i in sampleNames(gatingsetSYPROKP.hier)){
#   tiff(filename=paste0("Results/figures/",i,".tiff"),width=7,height = 7,
#        units = "in",res=900,
#        compression="lzw")
#   p <- autoplot(gatingsetSYPROKP.hier[[i]],bins=512)+theme_bw()
#   print(p)
#   dev.off()
# }
pSYPROSSCgates <- ggcyto(flowsetSYPROKP_transformed,
                    aes(y="SSC-H",x="BL2-H"))
pSYPROSSCgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateSYPROSSC,colour="darkgreen") 


pSYPROSSCgatesclean <- ggcyto(gatingsetSYPROKP.hier,
                    aes(y="SSC-H",x="BL2-H"),subset="root")
pSYPROSSCgatesclean + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateSYPROSSC,colour="darkgreen") 

pSYTOSSCgates <- ggcyto(flowsetSYPROKP_transformed,
                    aes(y="SSC-H",x="RL1-H"))
pSYTOSSCgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")


pSYPROFSCgates <- ggcyto(gatingsetSYPROKP.hier,
                    aes(y="FSC-H",x="BL2-H"),subset="root")
pSYPROFSCgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")

nodelistcl <- gs_get_pop_paths(gatingsetSYPROKP.hier.clean)

hierarchgsSYPROKP.clean <- gs_pop_get_data(gatingsetSYPROKP.hier.clean,
                                           nodelistcl[3])
hierarchfsSYPROKP.clean <- cytoset_to_flowSet(hierarchgsSYPROKP.clean)

## count, aggregate and annotate events for SYPRO after cleaning ----------------
countssypro <- fsApply(flowsetSYPROKP_transformed,nrow)
countssypro.clean <- fsApply(hierarchfsSYPROKP.clean,nrow)

cleanup.sypro.df <- data.frame(filenames=rownames(countssypro),
                               raw_events=countssypro,
                               cleaned_events=countssypro.clean)

cleanup.sypro.df.md <- dplyr::left_join(cleanup.sypro.df,mddf.toanalyze.SYPRO.MMMV.KP) %>%
                       pivot_longer(raw_events:cleaned_events,
                                    names_to="cleaning_status",
                                    values_to = "events")

cleanup.sypro.df.md$cleaning_status <- factor(cleanup.sypro.df.md$cleaning_status,
                                              levels=c("raw_events",
                                                      "cleaned_events"))

psyproclean <- cleanup.sypro.df.md %>% ggplot(aes(x=timepoint,
                                                  y=events,
                                                  fill=cleaning_status))
psyproclean + geom_boxplot() + theme_bw()

# BODIPY dataset ----------------------------------------------------------------
## ETL -------------------------------------------------------------------------
mddf.toanalyze.BODIPY.MMMV.KP <- mddf.toanalyze %>%
  dplyr::filter(target == "PHA" &
                  Medium == "MMMV" &
                  strain == "KP")
# only analyse data acquired with the new settings
mddf.toanalyze.BODIPY.MMMV.KP <- mddf.toanalyze.BODIPY.MMMV.KP[grep("newsettings",mddf.toanalyze.BODIPY.MMMV.KP$filenames),]

mddf.toanalyze.BODIPY.MMMV.KP$timepoint <- gsub(".*(t[0-9]).*.fcs","\\1",
                                      mddf.toanalyze.BODIPY.MMMV.KP$filenames)

flowsetBODIPYKP <- allfs.orig[mddf.toanalyze.BODIPY.MMMV.KP$filenames]

flowsetBODIPYKP.clean <- FCS_clean(flowsetBODIPYKP,
                                  param = c("BL1-H", "RL1-H",
                                            "SSC-H", "FSC-H"))

chnls <- colnames(flowsetBODIPYKP)[2:28]
transList <- transformerList(chnls,trans.obj)
gatingsetBODIPYKP <- GatingSet(flowsetBODIPYKP)
gatingsetBODIPYKP <- transform(gatingsetBODIPYKP, transList)
flowsetBODIPYKP_transformed <- cytoset_to_flowSet(gs_pop_get_data(gatingsetBODIPYKP))

gatingsetBODIPYKP.hier <- GatingSet(flowsetBODIPYKP)
gatingsetBODIPYKP.hier <- transform(gatingsetBODIPYKP.hier, transList)


gatingsetBODIPYKP.hier.clean <- GatingSet(flowsetBODIPYKP.clean)
gatingsetBODIPYKP.hier.clean <- transform(gatingsetBODIPYKP.hier.clean, transList)

## design gates ----------------------------------------------------------------
sqrcutBODIPYSYTO<- matrix(c(5.00, 5.00, 9.00, 15.0,11.0,
                            8.2, 12.5, 14.5, 14.5,7.40),
     ncol = 2,
     nrow = 5)
colnames(sqrcutBODIPYSYTO) <- c("BL1-H", "RL1-H")
polyGateBODIPYSYTO <- polygonGate(.gate = sqrcutBODIPYSYTO, filterId = "Dual positive")

sqrcutSYTOSSC<- matrix(c(7.50, 7.50, 10.0, 15.0,10,
                         7.50, 12.5, 14.5, 14.5,7.5),
     ncol = 2,
     nrow = 5)
colnames(sqrcutSYTOSSC) <- c("SSC-H", "RL1-H")
polyGateSYTOSSC <- polygonGate(.gate = sqrcutSYTOSSC, filterId = "SYTO62+")

sqrcutBODIPYSSC <- matrix(c(5.00, 12.5, 15.0, 5.00,
                            7.50, 7.50, 13.5, 13.5),
     ncol = 2,
     nrow = 4)
colnames(sqrcutBODIPYSSC) <- c("BL1-H", "SSC-H")
polyGateBODIPYSSC <- polygonGate(.gate = sqrcutBODIPYSSC, filterId = "BODIPY493+")

pSYTOSSCgates <- ggcyto(flowsetBODIPYKP_transformed,
                    aes(x="SSC-H",y="RL1-H"))
pSYTOSSCgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateSYTOSSC,colour="darkred")

pBODIPYSSCgates <- ggcyto(flowsetBODIPYKP_transformed,
                    aes(x="SSC-H",y="BL1-H"))
pBODIPYSSCgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateBODIPYSSC,colour="darkgreen") 

pBODIPYSYTOgates <- ggcyto(flowsetBODIPYKP_transformed,
                    aes(x="RL1-H",y="BL1-H"))
pBODIPYSYTOgates + geom_hex(bins=256) + theme_bw() + labs_cyto("marker")+ ggcyto_par_set(limits="instrument")+
            geom_gate(polyGateBODIPYSYTO,colour="orangered") 

nodes3 <- gs_pop_add(gatingsetBODIPYKP.hier,polyGateSYTOSSC)
nodes4 <- gs_pop_add(gatingsetBODIPYKP.hier,polyGateBODIPYSSC,parent="SYTO62+")
nodes5 <- gs_pop_add(gatingsetBODIPYKP.hier,polyGateBODIPYSYTO,parent="BODIPY493+")
recompute(gatingsetBODIPYKP.hier)
plot(gatingsetBODIPYKP.hier)

nodes3.clean <- gs_pop_add(gatingsetBODIPYKP.hier.clean,
                           polyGateSYTOSSC)
nodes4.clean <- gs_pop_add(gatingsetBODIPYKP.hier.clean,
                           polyGateBODIPYSSC,
                           parent="SYTO62+")
nodes5.clean <- gs_pop_add(gatingsetBODIPYKP.hier.clean,
                           polyGateBODIPYSYTO,
                           parent="BODIPY493+")
recompute(gatingsetBODIPYKP.hier.clean)
plot(gatingsetBODIPYKP.hier.clean)

# for(i in sampleNames(gatingsetBODIPYKP.hier)){
#   tiff(filename=paste0("Results/figures/",i,".tiff"),width=7,height = 7,
#        units = "in",res=900,
#        compression="lzw")
#   p <- autoplot(gatingsetBODIPYKP.hier[[i]],bins=256)+theme_bw()
#   print(p)
#   dev.off()
# }


nodelistclbp <- gs_get_pop_paths(gatingsetBODIPYKP.hier.clean)

hierarchgsBODIPYKP.clean <- gs_pop_get_data(gatingsetBODIPYKP.hier.clean,
                                           nodelistclbp[4])
hierarchfsBODIPYKP.clean <- cytoset_to_flowSet(hierarchgsBODIPYKP.clean)

## count, aggregate and annotate events for BODIPY after cleaning --------------
countsbodipy <- fsApply(flowsetBODIPYKP_transformed,nrow)
countsbodipy.clean <- fsApply(hierarchfsBODIPYKP.clean,nrow)

cleanup.bodipy.df <- data.frame(filenames=rownames(countsbodipy),
                               raw_events=countsbodipy,
                               cleaned_events=countsbodipy.clean)

cleanup.bodipy.df.md <- dplyr::left_join(cleanup.bodipy.df,
                                         mddf.toanalyze.BODIPY.MMMV.KP) %>%
                       pivot_longer(raw_events:cleaned_events,
                                    names_to="cleaning_status",
                                    values_to = "events")

cleanup.bodipy.df.md$cleaning_status <- factor(cleanup.bodipy.df.md$cleaning_status,
                                              levels=c("raw_events",
                                                      "cleaned_events"))

pbodipyclean <- cleanup.bodipy.df.md %>% ggplot(aes(x=timepoint,
                                                  y=events,
                                                  fill=cleaning_status))
pbodipyclean + geom_boxplot() + theme_bw()
```

### Results

##### SYPRO data cleaned

```{r sypromfires}
pd.clean <- phenoData(hierarchfsSYPROKP.clean)
mddf.sypro.clean <- mddf.toanalyze.SYPRO.MMMV.KP[mddf.toanalyze.SYPRO.MMMV.KP$filenames  %in% sampleNames(hierarchfsSYPROKP.clean),]
pd.clean$timepoint <- mddf.sypro.clean$timepoint
pd.clean$experiment <- mddf.sypro.clean$experiment
hierarchfsSYPRO.clean.atd <- hierarchfsSYPROKP.clean
phenoData(hierarchfsSYPRO.clean.atd) <- pd.clean

psypro.clean <- ggcyto(hierarchfsSYPRO.clean.atd,aes(x=`BL2-H`))
# psypro + geom_density(aes(y = ..count..,fill=Timepoint)) + facet_grid(Treatment~Timepoint)
psypro.clean + geom_density(aes(fill = timepoint), bw = "SJ") +
  facet_wrap(timepoint ~ experiment) +
  theme_bw() + coord_flip() +
  theme(axis.text.x = element_text(angle = 270)) + ylab("Density") +
  geom_vline(xintercept = 6.5,
             lty = 2,
             alpha = 0.6)

bpsypro.clean <- ggcyto(hierarchfsSYPRO.clean.atd, aes(y = `BL2-H`,
                                                       fill = timepoint))
bpsypro.clean + geom_violin(aes(x = 1), bw = "SJ") +
  facet_grid( ~ timepoint) +
  geom_hline(yintercept = 6.5,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

bpsypro.clean + geom_boxplot() + facet_grid(experiment ~ timepoint) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

medfluointenssypro_alone.clean <- gs_pop_get_stats(gatingsetSYPROKP.hier.clean,
                                             "/SYPRO+/Dual positive",
                                             type=pop.MFI)
reswb <- openxlsx::createWorkbook()
openxlsx::addWorksheet(reswb,sheetName = "MedianSypro_clean")
openxlsx::writeData(reswb,sheet="MedianSypro_clean",
                    x = medfluointenssypro_alone.clean)

meanfluointensSYPRO.clean <- fsApply(hierarchfsSYPRO.clean.atd,
                                     function(x)
                                       mean(x@exprs[, "BL2-H"]))
meanfluointensSYPRO.df.clean <-
  data.frame(filename = rownames(meanfluointensSYPRO.clean),
             mean_fluo_SYPRO = meanfluointensSYPRO.clean)

openxlsx::addWorksheet(reswb,sheetName = "MeanSypro_clean")
openxlsx::writeData(reswb,sheet="MeanSypro_clean",
                    x = meanfluointensSYPRO.df.clean)

```

#### SYTO62 MFI data clean

```{r sy62mfisyproclean, echo=FALSE,warning=FALSE,message=FALSE}

psyto.clean <- ggcyto(hierarchfsSYPRO.clean.atd, aes(x = `RL1-H`))
# psypro + geom_density(aes(y = ..count..,fill=Timepoint)) + facet_grid(Treatment~Timepoint)
psyto.clean + geom_density(aes(fill = timepoint), bw = "SJ") +
  facet_grid(experiment ~
               timepoint) +
  theme_bw() + coord_flip() +
  theme(axis.text.x = element_text(angle = 270)) +
  ylab("Density") +
  geom_vline(xintercept = 7,
             lty = 2,
             alpha = 0.6) + 
  labs_cyto("marker")
bpsyto.clean <- ggcyto(hierarchfsSYPRO.clean.atd,
                       aes(y = `RL1-H`, fill = timepoint))
bpsyto.clean + geom_violin(aes(x = 1), bw = "SJ") +
  facet_grid( ~ timepoint) +
  geom_hline(yintercept = 9,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )
bpsyto.clean + geom_boxplot() +
  facet_grid(experiment ~ timepoint) +
  geom_hline(yintercept = 7,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

medfluointenssypro.clean <- gs_pop_get_stats(gatingsetSYPROKP.hier.clean,
                                             "/SYPRO+",type=pop.MFI)
openxlsx::addWorksheet(reswb,sheetName = "MedianSyto62_Sypro_clean")
openxlsx::writeData(reswb,sheet="MedianSyto62_Sypro_clean",
                    x = medfluointenssypro.clean)

meanfluointenssyto62.clean <- fsApply(hierarchfsSYPRO.clean.atd,
                                function(x)mean(x@exprs[,"RL1-H"]))
meanfluointenssyto62.df.clean <-
  data.frame(filename=rownames(meanfluointenssyto62.clean),
             mean_fluo_syto62=meanfluointenssyto62.clean)
openxlsx::addWorksheet(reswb,sheetName = "MeanSyto62_Sypro_clean")
openxlsx::writeData(reswb,sheet="MeanSyto62_Sypro_clean",
                    x = meanfluointenssyto62.df.clean)
#openxlsx::saveWorkbook(reswb,file = "results/FcM_results.xlsx",overwrite = TRUE)
```

## PHA

##### BODIPY data

```{r BODIPYresultsclean,echo=FALSE,warning=FALSE,message=FALSE, fig.cap=c("Gaussian kernel density estimates of asinh transformed BL1-H (BODIPY) emission intensity (A.U.) of all gated cells (including all replicates) after acquisition-level cleanup using a bandwidth estimation by Sheather & Jones (1991) using pilot estimation of derivatives.Colored by timepoint, facetted by inital amount of N supplied. Dashed line included for reference purposes only. Axes are constant among facets to enhance comparability.","Gaussian kernel density violin plots of asinh transformed BL1-H (BODIPY) emission intensity (A.U.) of all gated cells (including all replicates) after acquisition-level cleanup using a bandwidth estimation by Sheather & Jones (1991) using pilot estimation of derivatives. Colored by timepoint, facetted by inital amount of N supplied. Dashed line included for reference purposes only. Axes are constant among facets to enhance comparability.","Box-and-whisker plots of asinh transformed BL2-H (BODIPY) emission intensity (A.U.) of all gated cells (including all replicates) after acquisition-level cleanup. Colored by timepoint, facetted by inital amount of N supplied. Axes are constant among facets to enhance comparability.")}
# add phenodata for flowViz::densityplot ---------------------------------------
pdclean <- phenoData(hierarchfsBODIPYKP.clean)

pdclean$timepoint <- mddf.toanalyze.BODIPY.MMMV.KP$timepoint
pdclean$experiment    <- mddf.toanalyze.BODIPY.MMMV.KP$experiment

hierarchfsBODIPY.clean.atd <- hierarchfsBODIPYKP.clean
phenoData(hierarchfsBODIPY.clean.atd) <- pdclean

pbodipyclean <- ggcyto(hierarchfsBODIPY.clean.atd,aes(x=`BL1-H`))
# psypro + geom_density(aes(y = ..count..,fill=Timepoint)) + facet_grid(Treatment~Timepoint)
pbodipyclean + geom_density(aes(fill = timepoint), bw = "SJ") +
  facet_grid(experiment ~ timepoint) +
  theme_bw() +
  coord_flip() +
  theme(axis.text.x = element_text(angle = 270)) +
  ylab("Density") +
  geom_vline(xintercept = 9,
             lty = 2,
             alpha = 0.6)
# pbodipy + geom_histogram(aes(fill=Timepoint),bins=100) + facet_grid(Treatment~Timepoint) + theme_bw()

bpbodipyclean <- ggcyto(hierarchfsBODIPY.clean.atd,
                        aes(y = `BL1-H`, fill = timepoint))
bpbodipyclean + geom_violin(aes(x = 1), bw = "SJ") +
  facet_grid( ~ timepoint) +
  geom_hline(yintercept = 9,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

bpbodipyclean + geom_boxplot() +
  facet_grid(experiment ~ timepoint) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )



medfluointensbodipy_alone.clean <-
  gs_pop_get_stats(gatingsetBODIPYKP.hier.clean,
                   "/SYTO62+/BODIPY493+/Dual positive",
                   type = pop.MFI)
openxlsx::addWorksheet(reswb, sheetName = "MedianBodipy_clean")
openxlsx::writeData(reswb, sheet = "MedianBodipy_clean",
                    x = medfluointensbodipy_alone.clean)

meanfluointensBODIPY.clean <- fsApply(hierarchfsBODIPY.clean.atd,
                                      function(x)
                                        mean(x@exprs[, "BL1-H"]))
meanfluointensBODIPY.clean.df <-
  data.frame(filename = rownames(meanfluointensBODIPY.clean),
             mean_fluo_SYPRO = meanfluointensBODIPY.clean)
openxlsx::addWorksheet(reswb, sheetName = "MeanBodipy_clean")
openxlsx::writeData(reswb, sheet = "MeanBodipy_clean",
                    x = meanfluointensBODIPY.clean.df)
```

##### SYTO62 MFI data

```{r sy62mfibodipyclean, echo=FALSE,warning=FALSE,message=FALSE,cache.lazy=FALSE}
pd62.clean <- phenoData(hierarchfsBODIPYKP.clean)
pd62.clean$experiment <- mddf.toanalyze.BODIPY.MMMV.KP$experiment
pd62.clean$timepoint <- mddf.toanalyze.BODIPY.MMMV.KP$timepoint


hierarchfsBODIPYKP.clean.atd <- hierarchfsBODIPYKP.clean
phenoData(hierarchfsBODIPYKP.clean.atd) <- pd62.clean


# grep("20201119_SYPRO_t0_CNECLMG1199_SYPROoSYTO62_C.nec_highN_SYPRO_t0_1.fcs",sampleNames(flowsetSYPRO_trf_subs_all.atd))
psytobpclean <- ggcyto(hierarchfsBODIPYKP.clean.atd,aes(x=`RL1-H`))
# psypro + geom_density(aes(y = ..count..,fill=Timepoint)) + facet_grid(Treatment~Timepoint)
psytobpclean + geom_density(aes(fill = timepoint), bw = "SJ") +
  facet_grid(experiment ~ timepoint) +
  theme_bw() +
  coord_flip() +
  theme(axis.text.x = element_text(angle = 270)) +
  ylab("Density") +
  geom_vline(xintercept = 10.5,
             lty = 2,
             alpha = 0.6) +
  labs_cyto("marker")

bpsytobpclean <- ggcyto(hierarchfsBODIPYKP.clean.atd,
                        aes(y = `RL1-H`, fill = timepoint))
bpsytobpclean + geom_violin(aes(x = 1), bw = "SJ") +
  facet_grid( ~ timepoint) +
  geom_hline(yintercept = 10.5,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

bpsytobpclean + geom_boxplot() +
  facet_grid(experiment ~ timepoint) +
  geom_hline(yintercept = 10.5,
             lty = 2,
             alpha = 0.6) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

medfluointensbodipy.clean <- gs_pop_get_stats(gatingsetBODIPYKP.hier.clean,
                                        "/SYTO62+",type=pop.MFI)
openxlsx::addWorksheet(reswb,sheetName = "MedianSyto62_BODIPY_clean")
openxlsx::writeData(reswb,sheet="MedianSyto62_BODIPY_clean",
                    x = medfluointensbodipy.clean)

meanfluointenssyto62BPclean <-
  fsApply(hierarchfsBODIPYKP.clean.atd,
          function(x)
            mean(x@exprs[, "RL1-H"]))
meanfluointenssyto62BPclean.df <-
  data.frame(filename = rownames(meanfluointenssyto62BPclean),
             mean_fluo_syto62 = meanfluointenssyto62BPclean)

openxlsx::addWorksheet(reswb,sheetName = "MeanSyto62_BODIPY_clean")
openxlsx::writeData(reswb,sheet="MeanSyto62_BODIPY_clean",
                    x = meanfluointenssyto62BPclean.df)
openxlsx::saveWorkbook(reswb,file = "Results/FCM_results.xlsx",overwrite = TRUE)
```

# Discussion